---
title: "RSF"
output: html_document
date: "2023-10-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}

### Prepare the work space
library(SpatialKDE)
library(tmap)
library(tmaptools)
library(tidyverse)
library(sp)
library(sf)
library(rgeos)
library(adehabitatMA)
library(digest)
library(mime)
library(jsonlite)
library(crs)
library(dplyr)
library(adehabitatHR)
library(Rcpp)
library(raster)
library(rgdal)
library(munsell)
library(tibble)
library(pillar)
library(ggplot2)
library(ResourceSelection)
library(mapview)
library(amt)
library(sjPlot)
library(Rgb)
library(nloptr)
library(colorspace)
library(rlang)
library(lattice)
library(MASS)
library(dismo)
library(scales)
library(rJava)
library(beepr)
library(OpenStreetMap)
library(lubridate)
library(rgdal)
library(munsell)
library(pillar)
library(ResourceSelection)
library(mapview)
library(amt)
library(sjPlot)
library(Rgb)
library(nloptr)
library(colorspace)
library(rlang)
library(broom) 
library(MASS)
library(ggmap)
library(gridExtra)
library(raster)
library(leaflet)
library(terra)
library(KernSmooth)
library(RColorBrewer)
library(cowplot)
library(colorBlindness)
library(kableExtra)
library(boot)
library(gclus)
library(lme4)


getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/Documents/1. PhD_Main/GitHub_link/Nittedal/SpatialAndMorphology_MBRA_MMYS"

output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs"

file.name <- "RSF"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today


```


```{r}

## Covariates from LiDAR data prepared by Hans Ole 
vars <- readRDS("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Inputs/SpatialData/vars_dist45.rds")

#Used and available positions - just for referencing. 
# rsf.data <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs/HomeRangeExploration_2023-09-28/used_available_pts_combined95KE.csv", 
#      col_types = cols(...1 = col_skip()))

summary(vars)
str(vars) # sf data frame
# 16522 observations of 47 variables 

names(vars)
# [1] "BatID"             "Easting"           "Northing"          "used"              "Species"          
#  [6] "UTM"      




# "Hmax"              "Hmean"             "Hsd"               "Hcv"              
# [11] "Hkurt"             "Hskewness"         

# "H10"               "H20"               "H30"              
# [16] "H40"               "H50"               "H60"               "H70"               "H80"              
# [21] "H90"               "H95"               




#"D0"                "D1"                "D2"               
# [26] "D3"                "D4"                "D5"                "D6"                "D7"               
# [31] "D8"                "D9"                


# "gap3.n"            "gap3.mean.area"    "gap3.sd.area"     
# [36] "gap3.sum.area"     "gap5.n"            "gap5.mean.area"    "gap5.sd.area"      "gap5.sum.area"    
# [41] "ttops.n"           "crown.mean.area"   "crown.sd.area"     "ttops.mean.height" "ttops.sd.height"  


# [46] "DIST"              "geom"   

```

# Housekeeping of LiDAR data 
```{r}

#Check correlations between pairs of lidar variables
# lidar.data <- vars[, 7:length(vars)]
# lidar.data <- as.data.frame(lidar.data) # convert from sf to standard df
# str(lidar.data) # need to remove "geom"
# lidar.data <- lidar.data %>% select(-geom)

# Make all columns numeric 
# lidar.data$gap3.n <- as.numeric(lidar.data$gap3.n)
# lidar.data$gap5.n <- as.numeric(lidar.data$gap5.n)
# lidar.data$ttops.n <- as.numeric(lidar.data$ttops.n)

# round(cor(lidar.data), 2)
# abs(cor(lidar.data))
# cor(lidar.data)
# # Error in cor(lidar.data) : 'x' must be numeric
# windows()
# pairs(lidar.data)
# Warning messages:
# 1: In doTryCatch(return(expr), name, parentenv, handler) :
#   display list redraw incomplete
# 2: In doTryCatch(return(expr), name, parentenv, handler) :
#   display list redraw incomplete
# 3: In doTryCatch(return(expr), name, parentenv, handler) :
#   display list redraw incomplete
# 4: In doTryCatch(return(expr), name, parentenv, handler) :
#   display list redraw incomplete
```



```{r}
## !! ## Katrine - do we still want to standardize lidar data to mean of zero? 

## yes 
vars$Species=as.factor(vars$Species)
vars$BatID=as.factor(vars$BatID)

vars$gap3.n <- as.numeric(vars$gap3.n)
vars$gap5.n <- as.numeric(vars$gap5.n)
vars$ttops.n <- as.numeric(vars$ttops.n)


# vars1 <- as.data.frame(vars) # cannot scale a spatial object 
# vars1[,7:46]=scale(vars1[,7:46],scale=TRUE)
# 
# 
# summary(vars1)
# str(vars1)
# names(vars)
# 
# vars2 <- drop_na(vars1)
# 
# # Have to drop NAs THEN scale variables to get an output. 
# 
# # 8473/16522
# # This is only half the observations 
# 
# vars3 <- drop_na(as.data.frame(vars)) 
# vars3[,7:46]=scale(vars3[,7:46],scale=TRUE)
# summary(vars3$used)
# vars3$f.used <- as.factor(vars3$used)
# summary(vars3$f.used)
# #    0    1 
# # 7558  915 
# 
# summary(vars3$BatID)
#   # Amelia   Aricia   Astrid    Dagny    Daisy    Ethel      Ida     Kaja     Line   Louise 
#   #     69      602      485      258     1069      658     1025        1      294      303 
#   #  Maren    Marie     Nora   Phoebe Ragnhild    Reeda    Sofia   Steffi    Stine     Thea 
#   #    686      192      296      394      140      713      273      147      347      458 
#   #  Turid 
#   #     63
# 
# ## Choose variables with *no* NAs instead. 

var1 <- vars %>% select(BatID, Easting, Northing, used, Species, Hmax, 
                        D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
                        gap3.mean.area, gap3.sum.area, 
                        gap5.n, gap5.mean.area, gap5.sum.area, 
                        ttops.n)
# 16522 obs of 23 vars 

summary(var1)
summary(var1$Hmax) # There are -Inf values which I will replace with 0 

var1$Hmax <- as.character(var1$Hmax)
var1 <- var1 %>% mutate(hmax = str_replace(Hmax, "-Inf", "0")) 
var1$hmax <- as.numeric(var1$hmax)

var1 <- var1 %>% select(-Hmax)

summary(var1$Hmax)

## Scale numeric variables to mean = 0 
var1 <- as.data.frame(var1)
# var1[,6:20]=scale(var1[,6:20],scale=TRUE) # returns NaN for Hmax
# Try scale(rep(1, 10))


# Make one large complex model with all variables

# If the NAs cause too many issues, discard all NAs and try again.

fit1 = glmer(used ~ Species + hmax + hmax*Species + (1|BatID), data=var1,
              family=binomial(link="logit"),nAGQ = 0) # that works! 

fit2 = glmer(used ~ Species + Hmean + Hmean*Species + (1|BatID), data=vars3,
              family=binomial(link="logit"),nAGQ = 0)

fit3 = glmer(used ~ Species + Hmean + Hmean*Species + (1|BatID), data=vars3,
              family=binomial(link="logit"),nAGQ = 0)

fit4 = glmer(used ~ Species + Hmean + Hmean*Species + (1|BatID), data=vars3,
              family=binomial(link="logit"),nAGQ = 0)

              Hsd + Hcv + Hkurt + Hskewness +
              H10 + H20 + H30 + H40 + 
              H50 + H60 + H70 + H80 + 
              H90 + H95 + D0 + D1 + D2 + 
              D3 + D4 + D5 + D6 + D7 + 
              D8 + D9 + gap3.n + gap3.mean.area +
              gap3.sd.area + gap3.sum.area + gap5.n + 
              gap5.mean.area + gap5.sd.area + gap5.sum.area + 
              ttops.n + crown.sd.area + crown.mean.area + 
              ttops.mean.height + ttops.sd.height +
              Hmax*Species + Hmean*Species + 
              Hsd*Species + Hcv*Species + Hkurt*Species + Hskewness*Species +
              H10*Species + H20*Species + H30*Species + H40*Species + 
              H50*Species + H60*Species + H70*Species + H80*Species + 
              H90*Species + H95*Species + D0*Species + D1*Species + D2*Species + 
              D3*Species + D4*Species + D5*Species + D6*Species + D7*Species + 
              D8*Species + D9*Species + gap3.n*Species + gap3.mean.area*Species +
              gap3.sd.area*Species + gap3.sum.area*Species + gap5.n*Species + 
              gap5.mean.area*Species + gap5.sd.area*Species + gap5.sum.area*Species + 
              ttops.n*Species + crown.sd.area*Species + crown.mean.area*Species + 
              ttops.mean.height*Species + ttops.sd.height*Species + (1|BatID), data=vars1,
              family=binomial(link="logit"),nAGQ = 0)
# Error: Invalid grouping factor specification, BatID
summary(vars1$BatID)



```


fit = glmer(used ~ Species + 
              Hmax*Species + Hmean*Species + 
              Hsd + Hcv + Hkurt + Hskewness +
              H10 + H20 + H30 + H40 + 
              H50 + H60 + H70 + H80 + 
              H90 + H95 + D0 + D1 + D2 + 
              D3 + D4 + D5 + D6 + D7 + 
              D8 + D9 + gap3.n + gap3.mean.area +
              gap3.sd.area + gap3.sum.area + gap5.n + 
              gap5.mean.area + gap5.sd.area + gap5.sum.area + 
              ttops.n + crown.sd.area + crown.mean.area + 
              ttops.mean.height + ttops.sd.height +
              Hmax*Species + Hmean*Species + 
              Hsd*Species + Hcv*Species + Hkurt*Species + Hskewness*Species +
              H10*Species + H20*Species + H30*Species + H40*Species + 
              H50*Species + H60*Species + H70*Species + H80*Species + 
              H90*Species + H95*Species + D0*Species + D1*Species + D2*Species + 
              D3*Species + D4*Species + D5*Species + D6*Species + D7*Species + 
              D8*Species + D9*Species + gap3.n*Species + gap3.mean.area*Species +
              gap3.sd.area*Species + gap3.sum.area*Species + gap5.n*Species + 
              gap5.mean.area*Species + gap5.sd.area*Species + gap5.sum.area*Species + 
              ttops.n*Species + crown.sd.area*Species + crown.mean.area*Species + 
              ttops.mean.height*Species + ttops.sd.height*Species + (1|BatID), data=vars1,
              family=binomial(link="logit"),nAGQ = 0)


<!-- #If the lidar variables are highly correlated:  -->
<!-- #Test each of them separately, in combination with Species and the lidar variable ? Species interaction -->


<!-- ```{r} -->
<!-- Mmys <- subset(vars, Species == "M.mystacinus") -->
<!-- Mbra <- subset(vars, Species == "M.brandtii") -->

<!-- #----------------Exploring lidar variables influencing probability of use in M_mys -->

<!-- #We will fit mixed models with BatID as random effect to account for among-individuals variation -->
<!-- fit1 = glmer(used ~ 1|BatID, data=Mmys, family=binomial(link="logit"), -->
<!--              nAGQ = 0)#Intercept model -->
<!-- fit2 = glmer(used ~ zmax + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)#zmax model - not taking into account which species -->
<!-- fit3 = glmer(used ~ zmean + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit4 = glmer(used ~ zsd + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit5 = glmer(used ~ pzabovezmean + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit6 = glmer(used ~ pzabove0.5 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit7 = glmer(used ~ zq10 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit8 = glmer(used ~ zq20 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit9 = glmer(used ~ zq30 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit10 = glmer(used ~ zq40 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit11 = glmer(used ~ zq50 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit12 = glmer(used ~ zq60 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit13 = glmer(used ~ zq70 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit14 = glmer(used ~ zq80 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit15 = glmer(used ~ zq90 + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit16 = glmer(used ~ zcv + (1|BatID), data=Mmys, -->
<!--               family=binomial(link="logit"),nAGQ = 0) -->
<!-- summary(fit1) -->
<!-- summary(fit2) -->
<!-- summary(fit3) -->
<!-- summary(fit4) -->
<!-- summary(fit5) -->
<!-- summary(fit6) -->
<!-- summary(fit7) -->
<!-- summary(fit8) -->
<!-- summary(fit9) -->
<!-- summary(fit10) -->
<!-- summary(fit11) -->
<!-- summary(fit12) -->
<!-- summary(fit13) -->
<!-- summary(fit14) -->
<!-- summary(fit15) -->
<!-- summary(fit16) -->


<!-- #                                         Fixed effects: -->
<!-- #                                  Estimate  Std. Error    z value Pr(>|z|)   -->
<!-- #summary(fit1)       (Intercept)  -0.001226    0.049523    -0.025     0.98 -->
<!-- #summary(fit2)       zmax          0.56845     0.05678     10.012   <2e-16 ***      -->
<!-- #summary(fit3)       zmean         0.28960     0.04925      5.881 4.08e-09 ***     -->
<!-- #summary(fit4)       zsd           0.37371     0.05079      7.358 1.87e-13 ***        -->
<!-- #summary(fit5)       pzabovezmean -0.104977    0.050002    -2.099     0.0358 * -->
<!-- #summary(fit6)       pzabove0.5    0.23349     0.05022      4.649 3.33e-06 *** -->
<!-- #summary(fit7)       zq10          1.08648    28.07220      0.039     0.969 -->
<!-- #summary(fit8)       zq20          0.067619    0.082128     0.823     0.410       -->
<!-- #summary(fit9)       zq30          0.062207    0.048318     1.287     0.198       -->
<!-- #summary(fit10)      zq40          0.11303     0.04620      2.447     0.0144 *       -->
<!-- #summary(fit11)      zq50          0.20342     0.04687      4.340 1.43e-05 ***       -->
<!-- #summary(fit12)      zq60          0.26371     0.04744      5.559 2.71e-08 ***      -->
<!-- #summary(fit13)      zq70          0.26479     0.04819      5.495 3.92e-08 ***       -->
<!-- #summary(fit14)      zq80          0.27160     0.04910      5.531 3.18e-08 ***       -->
<!-- #summary(fit15)      zq90          0.29352     0.04998      5.872 4.29e-09 ***       -->
<!-- #summary(fit16)      zcv           0.36400     0.06341      5.740 9.46e-09 ***        -->




<!-- #----------------Exploring lidar variables influencing probability of use in M_bra -->

<!-- #We will fit mixed models with BatID as random effect to account for among-individuals variation -->
<!-- fit1 = glmer(used ~ 1|BatID, data=Mbra, family=binomial(link="logit"), -->
<!--              nAGQ = 0)#Intercept model -->
<!-- fit2 = glmer(used ~ zmax + (1|BatID), data=Mbra, -->
<!--              family=binomial(link="logit"),nAGQ = 0)#zmax model - not taking into account which species -->
<!-- fit3 = glmer(used ~ zmean + (1|BatID), data=Mbra, -->
<!--              family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit4 = glmer(used ~ zsd + (1|BatID), data=Mbra, -->
<!--              family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit5 = glmer(used ~ pzabovezmean + (1|BatID), data=Mbra, -->
<!--              family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit6 = glmer(used ~ pzabove0.5 + (1|BatID), data=Mbra, -->
<!--              family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit7 = glmer(used ~ zq10 + (1|BatID), data=Mbra, -->
<!--              family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit8 = glmer(used ~ zq20 + (1|BatID), data=Mbra, -->
<!--              family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit9 = glmer(used ~ zq30 + (1|BatID), data=Mbra, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit10 = glmer(used ~ zq40 + (1|BatID), data=Mbra, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit11 = glmer(used ~ zq50 + (1|BatID), data=Mbra, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit12 = glmer(used ~ zq60 + (1|BatID), data=Mbra, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit13 = glmer(used ~ zq70 + (1|BatID), data=Mbra, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit14 = glmer(used ~ zq80 + (1|BatID), data=Mbra, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit15 = glmer(used ~ zq90 + (1|BatID), data=Mbra, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->
<!-- fit16 = glmer(used ~ zcv + (1|BatID), data=Mbra, -->
<!--               family=binomial(link="logit"),nAGQ = 0)# -->

<!-- summary(fit1) -->
<!-- summary(fit2) -->
<!-- summary(fit3) -->
<!-- summary(fit4) -->
<!-- summary(fit5) -->
<!-- summary(fit6) -->
<!-- summary(fit7) -->
<!-- summary(fit8) -->
<!-- summary(fit9) -->
<!-- summary(fit10) -->
<!-- summary(fit11) -->
<!-- summary(fit12) -->
<!-- summary(fit13) -->
<!-- summary(fit14) -->
<!-- summary(fit15) -->
<!-- summary(fit16) -->

<!-- #                                         Fixed effects: -->
<!-- #                                 Estimate Std. Error z value Pr(>|z|)   -->
<!-- #summary(fit1)      (Intercept)   -0.007315   0.054094  -0.135    0.892  -->
<!-- #summary(fit2)       zmax          0.59866    0.05753   10.406   <2e-16 ***     -->
<!-- #summary(fit3)       zmean         0.33770    0.06338    5.328 9.91e-08 ***    -->
<!-- #summary(fit4)       zsd           0.49433    0.06143    8.047 8.46e-16 ***       -->
<!-- #summary(fit5)       pzabovezmean -0.42778    0.05665   -7.551 4.31e-14 *** -->
<!-- #summary(fit6)       pzabove0.5    0.33931    0.05875    5.775 7.68e-09 *** -->
<!-- #summary(fit7)       zq10          2.55180    1.68871    1.511    0.131       -->
<!-- #summary(fit8)       zq20          0.139719   0.069896   1.999    0.0456 *      -->
<!-- #summary(fit9)       zq30          0.091476   0.060772   1.505    0.132      -->
<!-- #summary(fit10)      zq40          0.033818   0.062137   0.544    0.586      -->
<!-- #summary(fit11)      zq50          0.081969   0.062729   1.307    0.191      -->
<!-- #summary(fit12)      zq60          0.18005    0.06366    2.828    0.00468 **     -->
<!-- #summary(fit13)      zq70          0.31328    0.06315    4.961 7.01e-07 ***      -->
<!-- #summary(fit14)      zq80          0.36014    0.06187    5.821 5.85e-09 ***      -->
<!-- #summary(fit15)      zq90          0.40007    0.06042    6.622 3.55e-11 ***      -->
<!-- #summary(fit16)      zcv           0.28229    0.05259    5.367 7.99e-08 ***       -->


<!-- ``` -->

