---
title: "RSF"
output: html_document
date: "2023-10-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}

### Prepare the work space
library(tidyverse)
library(dplyr)
library(scales)
library(beepr)
library(lubridate)
library(ResourceSelection)
library(RColorBrewer)
library(cowplot)
library(colorBlindness)
library(kableExtra)
library(lme4)
library(stats)
library(DHARMa)
library(lattice)
library(broom)
library(modelsummary)
library(kableExtra)
library(gt)
library(readxl)
library(xlsx)
library(corrplot)
library(vegan)

getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/Documents/1. PhD_Main/GitHub_link/Nittedal/SpatialAndMorphology_MBRA_MMYS"

output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs"

file.name <- "RSF"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today


```


```{r}

## Covariates from LiDAR data prepared by Hans Ole 
vars <- readRDS("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Inputs/SpatialData/vars_dist45_v3.rds")

#Used and available positions - just for referencing. 
# rsf.data <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs/HomeRangeExploration_2023-09-28/used_available_pts_combined95KE.csv", 
#      col_types = cols(...1 = col_skip()))

summary(vars)
str(vars) # sf data frame
# 16522 observations of 47 variables 

names(vars)
# [1] "BatID"             "Easting"           "Northing"          "used"              "Species"          
#  [6] "UTM"               "Hmax"              "Hmean"             "Hsd"               "Hcv"              
# [11] "Hkurt"             "Hskewness"         "H10"               "H20"               "H30"              
# [16] "H40"               "H50"               "H60"               "H70"               "H80"              
# [21] "H90"               "H95"               "D0"                "D1"                "D2"               
# [26] "D3"                "D4"                "D5"                "D6"                "D7"               
# [31] "D8"                "D9"                "gap3.n"            "gap3.mean.area"    "gap3.sd.area"     
# [36] "gap3.sum.area"     "gap5.n"            "gap5.mean.area"    "gap5.sd.area"      "gap5.sum.area"    
# [41] "ttops.n"           "crown.mean.size"   "crown.sd.size"     "ttops.mean.height" "ttops.sd.height"  
# [46] "water.distance"    "water.objtype"     "YOD"               "DIST"              "geom"           

## For writing descriptions of each variable 

#mettext <- as.data.frame(names(vars))
# write.csv(mettext, "~mettext.csv") # 15.11.2023
```

# Housekeeping of LiDAR data 

```{r}
str(vars)
summary(vars)


# Hans Ole: HOW TO DEAL WITH NAs:
dt <- vars
summary(dt[is.na(dt$Hmean),])
dt$H10[is.na(dt$Hmax)] <- 0.5
dt$Hmean[is.na(dt$Hmean)] <- 0.5
dt$H10[is.na(dt$H10)] <- 0.5
dt$H20[is.na(dt$H20)] <- 0.5
dt$H30[is.na(dt$H30)] <- 0.5
dt$H40[is.na(dt$H40)] <- 0.5
dt$H50[is.na(dt$H50)] <- 0.5
dt$H60[is.na(dt$H60)] <- 0.5
dt$H70[is.na(dt$H70)] <- 0.5
dt$H80[is.na(dt$H80)] <- 0.5
dt$H90[is.na(dt$H90)] <- 0.5
dt$H95[is.na(dt$H95)] <- 0.5
set.seed(123)
un <- runif(10000)

dt$Hsd[is.na(dt$Hsd)] <- sd(un)
dt$Hcv[is.na(dt$Hcv)] <- dt$Hsd[is.na(dt$Hcv)] / dt$Hmean[is.na(dt$Hcv)]
dt$crown.mean.size[is.na(dt$crown.mean.size)] <- 0
dt$ttops.mean.height[is.na(dt$ttops.mean.height)] <- 0

dt$gap5.sd.area[is.na(dt$gap5.sd.area)] <- 0
dt$gap3.sd.area[is.na(dt$gap3.sd.area)] <- 0
dt$crown.sd.size[is.na(dt$crown.sd.size)] <- 0
dt$ttops.sd.height[is.na(dt$ttops.sd.height)] <- 0
summary(dt)

# Hmax -Inf = 0.5
dt$Hmax[dt$Hmax == "-Inf"] <- 0.5

## NAs for Hkurt and Hskewness: 
#  Generate a uniform distribution between 0 and 1 and compute the value of that

# Hkurt NA = -1.183527 
dt$Hkurt[is.na(dt$Hkurt)] <- -1.183527 

# Hskewness NA = 0.004507174 
dt$Hskewness[is.na(dt$Hskewness)] <- -0.004507174 


dt$Species=as.factor(dt$Species)
dt$BatID=as.factor(dt$BatID)
dt$water.objtype=as.factor(dt$water.objtype)

dt$YOD[is.na(dt$YOD)] <- "Undetected"
dt$YOD=as.factor(dt$YOD)


### Check for suspicious outliers
summary(dt)

# 16522 obs of 23 vars 
# There is an Hmax value of 99.77 m with the next highest value being ~30 m. This is some sort of miscalculation in the canopy height model, so it will be removed. (Available (used = 0) point for Astrid (MBRA)). 

## First convert to a normal dataframe(drop geoms/sf objects) 
dt1df <- as.data.frame(dt)
dt1df <- dt1df %>% select(-geom)
# 16484 obs of 49 vars



dt2df <- dt1df %>% dplyr::filter(Hmax < 90)
# 16483 obs of 49 vars

summary(dt2df)

## Are there any strong outliers amongst n of local maxima? 
hist(dt2df$ttops.n) 
# How does this look for used points? 
dt2dfused <- dt2df %>% filter(used == 1)
hist(dt2dfused$ttops.n) 
# what proportion of the dataset has a ttops.n value of less than 5? 
 
openareas <- dt2df %>% filter(ttops.n <= 5)
# 2377 obs 
2377/16483
# 14%
# How many of these open area observations are actual used points? 

summary(openareas)
table(openareas$used) # 17 points 
 
openused <- openareas %>% filter(used == 1 ) %>%  droplevels()

summary(openused)
table(openused$Species)
  # M.brandtii M.mystacinus 
  #          8            9 
table(openused$BatID)
# Amelia  Dagny  Ethel Louise Phoebe  Reeda Steffi  Stine   Thea 
#      2      1      2      2      5      1      1      2      1 



### Think of a way to more distinctly categorize "open areas". 


#### Scale continuous variables for ordination and modelling
dt1 <- dt2df # Use this to scale all continuous numerical data 
dt1[,7:46]=scale(dt1[,7:46], scale=TRUE) #
#
# names(dt1)


```


## Correlation/collinearity between LiDAR variables 
```{r}
# names(dt1)
# dtc <- dt1 %>% dplyr::select(c(
#   Hmax, Hmean, Hsd, Hcv, Hskewness, 
#   H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
#   D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
#   gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
#   gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
#   ttops.n, ttops.mean.height, ttops.sd.height)) 
# 
# windows()
# 
# corrplot(cor(dtc))
```



# NMDS ordination of available points to address collinearity and discern patterns in how variables influence each other 


### Prepare data for PCA 
```{r}

## Create an ID column so the bat meta data can be reattached later

## Create a unique row id which will become "idvar"

dt1$idvar <- paste0("ID-", 1:nrow(dt1)) 
headings <- dt1$idvar

## Now only includeLiDAR variables with IDvar
names(dt1)

dt2 <- dt1 %>% dplyr::select(c(
  Hmax, Hmean, Hsd, Hcv, Hskewness, Hkurt, 
  H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
  D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
  gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
  gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
  ttops.n, ttops.mean.height, ttops.sd.height)) 
## Remove hskewness for now because it has negative values... 
rownames(dt2) <- headings
# Reshape into wide format 

summary(dt2)
## This is a PCA, more info below: 

mat <- dt2 

### In case you want to do a PCA for only used points later 
# mat.used <- dt1 %>%
#   dplyr::filter(used == 1) %>% 
#   droplevels() %>% 
#   dplyr::select(c(
#   Hmax, Hmean, Hsd, Hcv, Hskewness, 
#   H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
#   D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
#   gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
#   gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
#   ttops.n, ttops.mean.height, ttops.sd.height)) 

```


## PCA
```{r}
## PCA 
trait.pca <- rda(mat) # used and available points together 

biplot(trait.pca) # simple plot 
screeplot(trait.pca) # how much of each axis describes the variation in the data 

summary(trait.pca)

pca.summary <- summary(trait.pca)

trait.loadings <- as.data.frame(pca.summary$species) %>% 
  mutate(trait = rownames(.))  
head(trait.loadings)



meta <- dt1 %>% dplyr::select(c(used, Species, idvar)) 
# for now, do not include bat.id

## Build meta data to be reattached in plotting
rownames(meta) <- meta$idvar
meta$gen.spe <- meta$idvar
meta$used <- as.factor(meta$used)

sp.scores <- as.data.frame(pca.summary$sites) %>% 
  mutate(gen.spe = rownames(.)) %>% inner_join(meta) 
# now used data is there

traittable <- trait.loadings  %>% 
  dplyr::select(trait, PC1, PC2)
#write.csv(traittable, file = file.path(output_today, "bothbats_allpts_PCA1_2_table.csv")) # 26.11.2023


spdf <- left_join(sp.scores, dt1, by = "idvar")
spdf1 <- spdf %>% dplyr::select(-c(PC3, PC4, PC5, PC6, idvar, gen.spe, used.x, used.y, Species.x, Species.y, BatID, Easting, Northing, UTM, YOD, DIST, water.distance, water.objtype))


#corrplot(cor(dtc))
cortab <- as.data.frame(cor(spdf1)) 

windows()
corrplot(cor(spdf1),
         tl.col="black", tl.srt=45,  
         type="lower", col=brewer.pal(n=5, name="Greys"))

cortab1 <- cortab[1:2,]
cortab2 <- t(cortab1)

#write.csv(cortab2, file = file.path(output_today, "cortab2.csv"))
# 28.11.2023

################################################################################
##### plotting 
################################################################################

## PC1 and PC2
pca.ggplot <- ggplot(data = sp.scores, aes(x = PC1, y = PC2)) +
  geom_point() +
  geom_segment(data = trait.loadings, 
               aes(x = 0, xend = PC1/2, y = 0, yend = PC2/2), lwd = 0.1) + # this is a new geom that allows you to draw segments like the ones for the loadings above
  geom_text(data = trait.loadings, aes(x = PC1/2, y = PC2/2+0.1, label = trait), size = 3) + # this adds text to the labels
  theme_bw() 
pca.ggplot

## PC1 and PC3
pca.ggplot <- ggplot(data = sp.scores, aes(x = PC1, y = PC3)) +
  geom_point() +
  geom_segment(data = trait.loadings, 
               aes(x = 0, xend = PC1/2, y = 0, yend = PC2/2), lwd = 0.1) + # this is a new geom that allows you to draw segments like the ones for the loadings above
  geom_text(data = trait.loadings, aes(x = PC1/2, y = PC2/2+0.1, label = trait), size = 3) + # this adds text to the labels
  theme_bw() 
pca.ggplot



#### More advanved plotting, with meta data 

cols <- c("0" = "gray", "1" = "red")
col2 <- c("MBRA" = "skyblue", "MMYS" = "darkblue")

## PC1 and PC2 - used is color 
pca.ggplot <- ggplot(data = sp.scores, aes(x = PC1, y = PC2)) +
  geom_point(aes(color = used), alpha = 0.3) +
  scale_color_manual(values = cols)+ 
  geom_segment(data = trait.loadings, 
               aes(x = 0, xend = PC1/2, y = 0, yend = PC2/2), lwd = 0.1) +
  geom_text(data = trait.loadings, aes(x = PC1/2, y = PC2/2+0.1, label = trait), size = 3) + 
  theme_bw() 
pca.ggplot

## PC1 and PC2 - used is color, separated by species 
pca.ggplot <- ggplot(data = sp.scores, aes(x = PC1, y = PC2)) +
  geom_point(aes(color = used), alpha = 0.3) +
  scale_color_manual(values = cols)+ 
  geom_segment(data = trait.loadings, 
               aes(x = 0, xend = PC1/2, y = 0, yend = PC2/2), lwd = 0.1) +
  geom_text(data = trait.loadings, aes(x = PC1/2, y = PC2/2+0.1, label = trait), size = 3) + facet_wrap(~Species) +
  theme_bw() 
pca.ggplot

## PC1 and PC2 - used is color, separated by species AND used
pca.ggplot <- ggplot(data = sp.scores, aes(x = PC1, y = PC2)) +
  geom_point(aes(color = used), alpha = 0.3) +
  scale_color_manual(values = cols)+ 
  geom_segment(data = trait.loadings, 
               aes(x = 0, xend = PC1/2, y = 0, yend = PC2/2), lwd = 0.1) +
  geom_text(data = trait.loadings, aes(x = PC1/2, y = PC2/2+0.1, label = trait), size = 3) + facet_wrap(used~Species) +
  theme_bw() 
pca.ggplot

```


# Model selection (explortatory approach)
We determined that the following covariates can be used to describe most of the variation in the LiDAR variables based on comparing the ordination of all LiDAR variables with PC1 and PC2, trait loadings and pearsons correlations coefficients between covariates and PC1:

H95
gap.sum.area (3 and 5)
gap.sd.area (3 and 5)
D0
Hsd

In addition we will include distance to water (dist.water) and bat ID as a random effect. 

I begin by modelling for each bat species separately with two candidate models - one with gap varaibles at 3 m and another with gap variables at 5 m. 


```{r}

## Simple models - separated by bat species, no species interaction 


# install.packages("lme4", type = "source") 
# library(lme4)
library(tidyverse)

MBRA <- dt1 %>% filter(Species == "M.brandtii") %>% droplevels() # 7633 obs of 49 vars
MMYS <- dt1 %>% filter(Species == "M.mystacinus") %>% droplevels() # 8850 obs of 49 vars

########################################################
########################  MBRA  ########################
########################################################
# Hmax
fit1MBRA= glmer(used ~  Hmax + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 


# Hmean
fit2MBRA = glmer(used ~ Hmean + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# Hsd 
fit3MBRA = glmer(used ~ Hsd + (1|BatID), data=dt1,
              family=binomial(link="logit"),nAGQ = 0) 

# Hcv
fit4MBRA = glmer(used ~ Hcv + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# Hkurt
fit5MBRA = glmer(used ~ Hkurt + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# Hskewness
fit6MBRA = glmer(used ~ Hskewness + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H10
fit7MBRA = glmer(used ~ H10 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H20
fit8MBRA = glmer(used ~ H20 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H30
fit9MBRA = glmer(used ~ H30 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H40
fit10MBRA = glmer(used ~ H40 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H50
fit11MBRA = glmer(used ~ H50  + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# H60
fit12MBRA = glmer(used ~ H60 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# H70
fit13MBRA = glmer(used ~ H70 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# H80
fit14MBRA = glmer(used ~ H80 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# H90
fit15MBRA = glmer(used ~ H90 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')

# H95
fit16MBRA = glmer(used ~ H95 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')


fit17MBRA = glmer(used ~ D0 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit18MBRA = glmer(used ~ D1 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit19MBRA = glmer(used ~ D2 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit20MBRA = glmer(used ~ D3 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit21MBRA = glmer(used ~ D4 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)

fit22MBRA = glmer(used ~ D5 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
#boundary (singular) fit: see help('isSingular')

fit23MBRA = glmer(used ~ D6 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit24MBRA = glmer(used ~ D7 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit25MBRA = glmer(used ~ D8 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit26MBRA = glmer(used ~ D9 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit27MBRA = glmer(used ~ gap3.n + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit28MBRA = glmer(used ~ gap3.mean.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit29MBRA = glmer(used ~ gap3.sd.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit30MBRA = glmer(used ~ gap3.sum.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit31MBRA = glmer(used ~  gap5.n + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit32MBRA = glmer(used ~ gap5.mean.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit33MBRA = glmer(used ~ gap5.sd.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit34MBRA = glmer(used ~ gap5.sum.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit35MBRA = glmer(used ~ ttops.n + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit36MBRA = glmer(used ~ crown.mean.size + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit37MBRA = glmer(used ~ crown.sd.size + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit38MBRA = glmer(used ~ ttops.mean.height + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit39MBRA = glmer(used ~ ttops.sd.height + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit40MBRA = glmer(used ~ water.distance + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)

# NOTE: 
# error message "boundary (singular) fit: see help('isSingular')" interpretted as: 
# Your model did fit, but it generated that warning because your random effects are very small. 

################################################################################


########################################################
########################  MMYS  ########################
########################################################
# Hmax
fit1MMYS= glmer(used ~  Hmax + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# Hmean
fit2MMYS = glmer(used ~ Hmean + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# Hsd 
fit3MMYS = glmer(used ~ Hsd + (1|BatID), data=dt1,
              family=binomial(link="logit"),nAGQ = 0) 

# Hcv
fit4MMYS = glmer(used ~ Hcv + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# Hkurt
fit5MMYS = glmer(used ~ Hkurt + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# Hskewness
fit6MMYS = glmer(used ~ Hskewness + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H10
fit7MMYS = glmer(used ~ H10 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H20
fit8MMYS = glmer(used ~ H20 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H30
fit9MMYS = glmer(used ~ H30 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H40
fit10MMYS = glmer(used ~ H40 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H50
fit11MMYS = glmer(used ~ H50  + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# H60
fit12MMYS = glmer(used ~ H60 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# H70
fit13MMYS = glmer(used ~ H70 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# H80
fit14MMYS = glmer(used ~ H80 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# H90
fit15MMYS = glmer(used ~ H90 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')

# H95
fit16MMYS = glmer(used ~ H95 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')


fit17MMYS = glmer(used ~ D0 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit18MMYS = glmer(used ~ D1 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit19MMYS = glmer(used ~ D2 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit20MMYS = glmer(used ~ D3 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit21MMYS = glmer(used ~ D4 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)

fit22MMYS = glmer(used ~ D5 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
#boundary (singular) fit: see help('isSingular')

fit23MMYS = glmer(used ~ D6 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit24MMYS = glmer(used ~ D7 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit25MMYS = glmer(used ~ D8 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit26MMYS = glmer(used ~ D9 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit27MMYS = glmer(used ~ gap3.n + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit28MMYS = glmer(used ~ gap3.mean.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit29MMYS = glmer(used ~ gap3.sd.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit30MMYS = glmer(used ~ gap3.sum.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit31MMYS = glmer(used ~  gap5.n + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit32MMYS = glmer(used ~ gap5.mean.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit33MMYS = glmer(used ~ gap5.sd.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit34MMYS = glmer(used ~ gap5.sum.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit35MMYS = glmer(used ~ ttops.n + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit36MMYS = glmer(used ~ crown.mean.size + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit37MMYS = glmer(used ~ crown.sd.size + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit38MMYS = glmer(used ~ ttops.mean.height + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit39MMYS = glmer(used ~ ttops.sd.height + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit40MMYS = glmer(used ~ water.distance + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)


```


# Summary tables
```{r}

fitlist <- list(
             fit1MBRA, fit1MMYS, fit2MBRA, fit2MMYS,
             fit3MBRA, fit3MMYS, fit4MBRA, fit4MMYS,
             fit5MBRA, fit5MMYS, fit6MBRA, fit6MMYS,
             fit7MBRA, fit7MMYS, fit8MBRA, fit8MMYS,
             fit9MBRA, fit9MMYS, fit10MBRA, fit10MMYS,
             fit11MBRA, fit11MMYS,
             fit12MBRA, fit12MMYS, fit13MBRA, fit13MMYS,
             fit14MBRA, fit14MMYS, fit15MBRA, fit15MMYS,
             fit16MBRA, fit16MMYS, fit17MBRA, fit17MMYS,
             fit18MBRA, fit18MMYS, fit19MBRA, fit19MMYS,
             fit20MBRA, fit20MMYS,
             fit21MBRA, fit21MMYS, fit22MBRA, fit22MMYS,
             fit23MBRA, fit23MMYS, fit24MBRA, fit24MMYS,
             fit25MBRA, fit25MMYS, fit26MBRA, fit26MMYS,
             fit27MBRA, fit27MMYS, fit28MBRA, fit28MMYS,
             fit29MBRA, fit29MMYS, fit30MBRA, fit30MMYS,
             fit31MBRA, fit31MMYS, fit32MBRA, fit32MMYS,
             fit33MBRA, fit33MMYS, fit34MBRA, fit34MMYS,
             fit35MBRA, fit35MMYS, fit36MBRA, fit36MMYS,
             fit37MBRA, fit37MMYS, fit38MBRA, fit38MMYS,
             fit39MBRA, fit39MMYS, fit40MBRA, fit40MMYS)

# Combine summary outputs to view them all at once 

modelsums <- modelsummary(fitlist, statistic = 'p.value', output = "data.frame") 

write.xlsx(modelsums, file = file.path(output_today, "allfits_bothspecies_models.xlsx")) 

```


## Check correlation of fixed effects
```{r}
names(dt2)
dt3 <- dt2 %>% dplyr::select(c(
  Hmax, Hmean, Hsd, Hcv, Hskewness, 
  H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
  D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
  gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
  gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
  ttops.n, ttops.mean.height, ttops.sd.height)) 

windows()
library(corrplot)
corrplot(cor(dt3))



library(performance)
summary(fit1)
print(fit1, correlation=TRUE) 

check_model(fit1) 


vc <- vcov(fit1)

# diagonal matrix of standard deviations associated with vcov
S <- sqrt(diag(diag(vc), nrow(vc), nrow(vc)))

# convert vc to a correlation matrix
solve(S) %*% vc %*% solve(S)


testDispersion(fit1)

simulationOutput <- simulateResiduals(fittedModel = fit1, plot = F)
residuals(simulationOutput)

residuals(simulationOutput, quantileFunction = qnorm, outlierValues = c(-7,7))

plot(simulationOutput)

testDispersion(simulationOutput)

# testSpatialAutocorrelation(simulationOutput = simulationOutput, x = dt1$Easting, y= dt2$Northing) - this does not work 
```


## Sketch model fit for model  to understand what the model is telling us 

Ran into issues with using the glm() function. From what I could read online troubleshooting this error may involve uninstalling and reinstalling R which I would like to avoid... 
```{r}
############################################################

##refitting model with GLM to sketch results

fit.x <- glm(used ~ Species + hmax + D7 + 
              gap3.sum.area +
              gap5.mean.area +
              gap5.n +
              hmax*Species +
              D7*Species +
              gap3.sum.area*Species +
              gap5.n*Species, family=binomial(), data=var1)

summary(fit.x)
# Coefficients:
#                                    Estimate Std. Error z value Pr(>|z|)    
# (Intercept)                       -3.123896   0.177948 -17.555  < 2e-16 ***
# SpeciesM.mystacinus               -0.471452   0.245765  -1.918 0.055072 .  
# hmax                               0.064046   0.006310  10.150  < 2e-16 ***
# D8                                -1.528826   0.339763  -4.500 6.81e-06 ***
# gap3.sum.area                     -0.936956   0.149551  -6.265 3.73e-10 ***
# gap5.mean.area                    -0.202879   0.058935  -3.442 0.000577 ***
# ttops.n                           -0.012984   0.001790  -7.254 4.03e-13 ***
# gap5.n                            -0.290077   0.087132  -3.329 0.000871 ***
# D7                                 1.022709   0.358025   2.857 0.004283 ** 
# SpeciesM.mystacinus:hmax           0.020468   0.009897   2.068 0.038627 *  
# SpeciesM.mystacinus:D7             0.848583   0.142466   5.956 2.58e-09 ***
# SpeciesM.mystacinus:gap3.sum.area  1.079950   0.168810   6.397 1.58e-10 ***
# SpeciesM.mystacinus:gap5.n         0.418130   0.112878   3.704 0.000212 ***
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# (Dispersion parameter for binomial family taken to be 1)
# 
#     Null deviance: 10066.4  on 16521  degrees of freedom
# Residual deviance:  9567.8  on 16509  degrees of freedom
# AIC: 9593.8
# 
# Number of Fisher Scoring iterations: 6


##getting predicted use as a function of zmax, at average zq60 and zcv
range.hmax <- range(var1$hmax)
range.hmax
#[1] 0.00 99.77

plotting_dfm <- expand.grid(hmax = seq(from = 0, to = 99.7, by = 10),
                            Species    = c("M.brandtii","M.mystacinus"),
                            D7 = mean(var1$D7),
                            gap3.sum.area = mean(var1$gap3.sum.area),
                            gap3.mean.area = mean(var1$gap3.mean.area),
                            gap5.mean.area = mean(var1$gap5.mean.area), 
                            gap5.n = mean(var1$gap5.n))

plotting_dfm$Species = as.factor(plotting_dfm$Species)

plotting_dfm$preds <- plogis( predict(fit.x , newdata=plotting_dfm))

 
##plotting the predicted response on the two covariates
windows()
pl <- ggplot(plotting_dfm, aes(x=hmax, y =preds, color=as.factor(Species)))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by hmax and Species") + 
  ggplot2::ylab("Predicted Use")


#----------------------------- gap5.n 

##getting predicted use as a function of zq60, at average zmax and zcv
range.gap5.n <- range(var1$gap5.n)
range.gap5.n
#[1] -0.6713285  5.7284651

plotting_dfm <- expand.grid(gap5.n = seq(from = -0.67, to = 5.73, by = 0.2),
                            Species    = c("M.brandtii","M.mystacinus"),
                            D7 = mean(var1$D7),
                            gap3.sum.area = mean(var1$gap3.sum.area),
                            gap3.mean.area = mean(var1$gap3.mean.area),
                            gap5.mean.area = mean(var1$gap5.mean.area), 
                            hmax = mean(var1$hmax))

plotting_dfm$Species = as.factor(plotting_dfm$Species)

plotting_dfm$preds <- plogis( predict(fit.x , newdata=plotting_dfm))


##plotting the predicted response on the two covariates
windows()
pl <- ggplot(plotting_dfm, aes(x=gap5.n, y =preds, color=as.factor(Species)))
pl + 
  geom_point( ) +
  geom_smooth() + 
  ggtitle("Predicted Use by gap5.n and Species") + 
  ggplot2::ylab("Predicted Use")








```

