---
title: "RSF"
output: html_document
date: "2023-10-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}

### Prepare the work space
library(tidyverse)
library(dplyr)
library(scales)
library(beepr)
library(lubridate)
library(ResourceSelection)
library(RColorBrewer)
library(cowplot)
library(colorBlindness)
library(kableExtra)
library(lme4)
library(stats)
library(DHARMa)
library(lattice)
library(broom)
library(modelsummary)
library(kableExtra)
library(gt)
library(readxl)
library(xlsx)

getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/Documents/1. PhD_Main/GitHub_link/Nittedal/SpatialAndMorphology_MBRA_MMYS"

output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs"

file.name <- "RSF"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today


```


```{r}

## Covariates from LiDAR data prepared by Hans Ole 
vars <- readRDS("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Inputs/SpatialData/vars_dist45_v3.rds")

#Used and available positions - just for referencing. 
# rsf.data <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs/HomeRangeExploration_2023-09-28/used_available_pts_combined95KE.csv", 
#      col_types = cols(...1 = col_skip()))

summary(vars)
str(vars) # sf data frame
# 16522 observations of 47 variables 

names(vars)
# [1] "BatID"             "Easting"           "Northing"          "used"              "Species"          
#  [6] "UTM"               "Hmax"              "Hmean"             "Hsd"               "Hcv"              
# [11] "Hkurt"             "Hskewness"         "H10"               "H20"               "H30"              
# [16] "H40"               "H50"               "H60"               "H70"               "H80"              
# [21] "H90"               "H95"               "D0"                "D1"                "D2"               
# [26] "D3"                "D4"                "D5"                "D6"                "D7"               
# [31] "D8"                "D9"                "gap3.n"            "gap3.mean.area"    "gap3.sd.area"     
# [36] "gap3.sum.area"     "gap5.n"            "gap5.mean.area"    "gap5.sd.area"      "gap5.sum.area"    
# [41] "ttops.n"           "crown.mean.size"   "crown.sd.size"     "ttops.mean.height" "ttops.sd.height"  
# [46] "water.distance"    "water.objtype"     "YOD"               "DIST"              "geom"           

## For writing descriptions of each variable 

#mettext <- as.data.frame(names(vars))
# write.csv(mettext, "~mettext.csv") # 15.11.2023
```

# Housekeeping of LiDAR data 

```{r}
str(vars)
summary(vars)


# Hans Ole: HOW TO DEAL WITH NAs:
dt <- vars
summary(dt[is.na(dt$Hmean),])
dt$H10[is.na(dt$Hmax)] <- 0.5
dt$Hmean[is.na(dt$Hmean)] <- 0.5
dt$H10[is.na(dt$H10)] <- 0.5
dt$H20[is.na(dt$H20)] <- 0.5
dt$H30[is.na(dt$H30)] <- 0.5
dt$H40[is.na(dt$H40)] <- 0.5
dt$H50[is.na(dt$H50)] <- 0.5
dt$H60[is.na(dt$H60)] <- 0.5
dt$H70[is.na(dt$H70)] <- 0.5
dt$H80[is.na(dt$H80)] <- 0.5
dt$H90[is.na(dt$H90)] <- 0.5
dt$H95[is.na(dt$H95)] <- 0.5
set.seed(123)
un <- runif(10000)

dt$Hsd[is.na(dt$Hsd)] <- sd(un)
dt$Hcv[is.na(dt$Hcv)] <- dt$Hsd[is.na(dt$Hcv)] / dt$Hmean[is.na(dt$Hcv)]
dt$crown.mean.size[is.na(dt$crown.mean.size)] <- 0
dt$ttops.mean.height[is.na(dt$ttops.mean.height)] <- 0

dt$gap5.sd.area[is.na(dt$gap5.sd.area)] <- 0
dt$gap3.sd.area[is.na(dt$gap3.sd.area)] <- 0
dt$crown.sd.size[is.na(dt$crown.sd.size)] <- 0
dt$ttops.sd.height[is.na(dt$ttops.sd.height)] <- 0
summary(dt)

# Hmax -Inf = 0.5
dt$Hmax[dt$Hmax == "-Inf"] <- 0.5

## NAs for Hkurt and Hskewness: 
#  Generate a uniform distribution between 0 and 1 and compute the value of that

# Hkurt NA = -1.183527 
dt$Hkurt[is.na(dt$Hkurt)] <- -1.183527 

# Hskewness NA = 0.004507174 
dt$Hskewness[is.na(dt$Hskewness)] <- -0.004507174 


dt$Species=as.factor(dt$Species)
dt$BatID=as.factor(dt$BatID)
dt$water.objtype=as.factor(dt$water.objtype)

dt$YOD[is.na(dt$YOD)] <- "Undetected"
dt$YOD=as.factor(dt$YOD)

# 16522 obs of 23 vars 

dt1 <- dt # Use this to scale all continuous numerical data besides distance to water 

dt1[,7:46]=scale(dt1[,7:46], scale=TRUE) #

names(dt1)


```

# Model selection 
- Start by fitting a simplified model for each LiDAR and environmental variable 
- Compare the summaries of these models to find which variables have some influence on bat species presence
- Select variables that have some influence on the bat species presence to create a more complex model. 
- Use the drop1() function to create the least complex / most complex model. 

```{r}

## Simple models - separated by bat species, no species interaction 

dt2 <- as_tibble(dt1 %>% select(-geom)) # remove geom to convert back to a standard tibble 
MBRA <- dt2 %>% filter(Species == "M.brandtii") %>% droplevels() # 7634 obs of 49 vars
MMYS <- dt2 %>% filter(Species == "M.mystacinus") %>% droplevels() # 8850 obs of 49 vars

########################################################
########################  MBRA  ########################
########################################################
# Hmax
fit1MBRA= glmer(used ~  Hmax + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# Hmean
fit2MBRA = glmer(used ~ Hmean + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# Hsd 
fit3MBRA = glmer(used ~ Hsd + (1|BatID), data=dt1,
              family=binomial(link="logit"),nAGQ = 0) 

# Hcv
fit4MBRA = glmer(used ~ Hcv + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# Hkurt
fit5MBRA = glmer(used ~ Hkurt + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# Hskewness
fit6MBRA = glmer(used ~ Hskewness + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H10
fit7MBRA = glmer(used ~ H10 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H20
fit8MBRA = glmer(used ~ H20 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H30
fit9MBRA = glmer(used ~ H30 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H40
fit10MBRA = glmer(used ~ H40 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H50
fit11MBRA = glmer(used ~ H50  + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# H60
fit12MBRA = glmer(used ~ H60 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# H70
fit13MBRA = glmer(used ~ H70 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# H80
fit14MBRA = glmer(used ~ H80 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

# H90
fit15MBRA = glmer(used ~ H90 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')

# H95
fit16MBRA = glmer(used ~ H95 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')


fit17MBRA = glmer(used ~ D0 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit18MBRA = glmer(used ~ D1 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit19MBRA = glmer(used ~ D2 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit20MBRA = glmer(used ~ D3 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit21MBRA = glmer(used ~ D4 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)

fit22MBRA = glmer(used ~ D5 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
#boundary (singular) fit: see help('isSingular')

fit23MBRA = glmer(used ~ D6 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit24MBRA = glmer(used ~ D7 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit25MBRA = glmer(used ~ D8 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit26MBRA = glmer(used ~ D9 + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit27MBRA = glmer(used ~ gap3.n + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit28MBRA = glmer(used ~ gap3.mean.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit29MBRA = glmer(used ~ gap3.sd.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit30MBRA = glmer(used ~ gap3.sum.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit31MBRA = glmer(used ~  gap5.n + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit32MBRA = glmer(used ~ gap5.mean.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit33MBRA = glmer(used ~ gap5.sd.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit34MBRA = glmer(used ~ gap5.sum.area + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit35MBRA = glmer(used ~ ttops.n + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit36MBRA = glmer(used ~ crown.mean.size + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit37MBRA = glmer(used ~ crown.sd.size + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit38MBRA = glmer(used ~ ttops.mean.height + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit39MBRA = glmer(used ~ ttops.sd.height + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit40MBRA = glmer(used ~ water.distance + (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0)

# NOTE: 
# error message "boundary (singular) fit: see help('isSingular')" interpretted as: 
# Your model did fit, but it generated that warning because your random effects are very small. 

################################################################################


########################################################
########################  MMYS  ########################
########################################################
# Hmax
fit1MMYS= glmer(used ~  Hmax + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# Hmean
fit2MMYS = glmer(used ~ Hmean + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# Hsd 
fit3MMYS = glmer(used ~ Hsd + (1|BatID), data=dt1,
              family=binomial(link="logit"),nAGQ = 0) 

# Hcv
fit4MMYS = glmer(used ~ Hcv + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# Hkurt
fit5MMYS = glmer(used ~ Hkurt + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# Hskewness
fit6MMYS = glmer(used ~ Hskewness + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H10
fit7MMYS = glmer(used ~ H10 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H20
fit8MMYS = glmer(used ~ H20 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H30
fit9MMYS = glmer(used ~ H30 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H40
fit10MMYS = glmer(used ~ H40 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular') 

# H50
fit11MMYS = glmer(used ~ H50  + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# H60
fit12MMYS = glmer(used ~ H60 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# H70
fit13MMYS = glmer(used ~ H70 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# H80
fit14MMYS = glmer(used ~ H80 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

# H90
fit15MMYS = glmer(used ~ H90 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')

# H95
fit16MMYS = glmer(used ~ H95 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')


fit17MMYS = glmer(used ~ D0 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit18MMYS = glmer(used ~ D1 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit19MMYS = glmer(used ~ D2 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit20MMYS = glmer(used ~ D3 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit21MMYS = glmer(used ~ D4 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)

fit22MMYS = glmer(used ~ D5 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
#boundary (singular) fit: see help('isSingular')

fit23MMYS = glmer(used ~ D6 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit24MMYS = glmer(used ~ D7 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit25MMYS = glmer(used ~ D8 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit26MMYS = glmer(used ~ D9 + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit27MMYS = glmer(used ~ gap3.n + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit28MMYS = glmer(used ~ gap3.mean.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit29MMYS = glmer(used ~ gap3.sd.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit30MMYS = glmer(used ~ gap3.sum.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit31MMYS = glmer(used ~  gap5.n + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit32MMYS = glmer(used ~ gap5.mean.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit33MMYS = glmer(used ~ gap5.sd.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit34MMYS = glmer(used ~ gap5.sum.area + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular')

fit35MMYS = glmer(used ~ ttops.n + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit36MMYS = glmer(used ~ crown.mean.size + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit37MMYS = glmer(used ~ crown.sd.size + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit38MMYS = glmer(used ~ ttops.mean.height + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit39MMYS = glmer(used ~ ttops.sd.height + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)
# boundary (singular) fit: see help('isSingular') 

fit40MMYS = glmer(used ~ water.distance + (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0)


```


# Summary tables
```{r}

fitlist <- list(
             fit1MBRA, fit1MMYS, fit2MBRA, fit2MMYS,
             fit3MBRA, fit3MMYS, fit4MBRA, fit4MMYS,
             fit5MBRA, fit5MMYS, fit6MBRA, fit6MMYS,
             fit7MBRA, fit7MMYS, fit8MBRA, fit8MMYS,
             fit9MBRA, fit9MMYS, fit10MBRA, fit10MMYS,
             fit11MBRA, fit11MMYS,
             fit12MBRA, fit12MMYS, fit13MBRA, fit13MMYS,
             fit14MBRA, fit14MMYS, fit15MBRA, fit15MMYS,
             fit16MBRA, fit16MMYS, fit17MBRA, fit17MMYS,
             fit18MBRA, fit18MMYS, fit19MBRA, fit19MMYS,
             fit20MBRA, fit20MMYS,
             fit21MBRA, fit21MMYS, fit22MBRA, fit22MMYS,
             fit23MBRA, fit23MMYS, fit24MBRA, fit24MMYS,
             fit25MBRA, fit25MMYS, fit26MBRA, fit26MMYS,
             fit27MBRA, fit27MMYS, fit28MBRA, fit28MMYS,
             fit29MBRA, fit29MMYS, fit30MBRA, fit30MMYS,
             fit31MBRA, fit31MMYS, fit32MBRA, fit32MMYS,
             fit33MBRA, fit33MMYS, fit34MBRA, fit34MMYS,
             fit35MBRA, fit35MMYS, fit36MBRA, fit36MMYS,
             fit37MBRA, fit37MMYS, fit38MBRA, fit38MMYS,
             fit39MBRA, fit39MMYS, fit40MBRA, fit40MMYS)

# Combine summary outputs to view them all at once 

modelsums <- modelsummary(fitlist, statistic = 'p.value', output = "data.frame") 

write.xlsx(modelsums, file = file.path(output_today, "allfits_bothspecies_models.xlsx")) 

```


## Check correlation of fixed effects
```{r}
names(dt2)
dt3 <- dt2 %>% dplyr::select(c(
  Hmax, Hmean, Hsd, Hcv, Hskewness, 
  H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
  D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
  gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
  gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
  ttops.n, ttops.mean.height, ttops.sd.height)) 

windows()
library(corrplot)
corrplot(cor(dt3))



library(performance)
summary(fit1)
print(fit1, correlation=TRUE) 

check_model(fit1) 


vc <- vcov(fit1)

# diagonal matrix of standard deviations associated with vcov
S <- sqrt(diag(diag(vc), nrow(vc), nrow(vc)))

# convert vc to a correlation matrix
solve(S) %*% vc %*% solve(S)


testDispersion(fit1)

simulationOutput <- simulateResiduals(fittedModel = fit1, plot = F)
residuals(simulationOutput)

residuals(simulationOutput, quantileFunction = qnorm, outlierValues = c(-7,7))

plot(simulationOutput)

testDispersion(simulationOutput)

# testSpatialAutocorrelation(simulationOutput = simulationOutput, x = dt1$Easting, y= dt2$Northing) - this does not work 
```


## Sketch model fit for model  to understand what the model is telling us 

Ran into issues with using the glm() function. From what I could read online troubleshooting this error may involve uninstalling and reinstalling R which I would like to avoid... 
```{r}
############################################################

##refitting model with GLM to sketch results

fit.x <- glm(used ~ Species + hmax + D7 + 
              gap3.sum.area +
              gap5.mean.area +
              gap5.n +
              hmax*Species +
              D7*Species +
              gap3.sum.area*Species +
              gap5.n*Species, family=binomial(), data=var1)

summary(fit.x)
# Coefficients:
#                                    Estimate Std. Error z value Pr(>|z|)    
# (Intercept)                       -3.123896   0.177948 -17.555  < 2e-16 ***
# SpeciesM.mystacinus               -0.471452   0.245765  -1.918 0.055072 .  
# hmax                               0.064046   0.006310  10.150  < 2e-16 ***
# D8                                -1.528826   0.339763  -4.500 6.81e-06 ***
# gap3.sum.area                     -0.936956   0.149551  -6.265 3.73e-10 ***
# gap5.mean.area                    -0.202879   0.058935  -3.442 0.000577 ***
# ttops.n                           -0.012984   0.001790  -7.254 4.03e-13 ***
# gap5.n                            -0.290077   0.087132  -3.329 0.000871 ***
# D7                                 1.022709   0.358025   2.857 0.004283 ** 
# SpeciesM.mystacinus:hmax           0.020468   0.009897   2.068 0.038627 *  
# SpeciesM.mystacinus:D7             0.848583   0.142466   5.956 2.58e-09 ***
# SpeciesM.mystacinus:gap3.sum.area  1.079950   0.168810   6.397 1.58e-10 ***
# SpeciesM.mystacinus:gap5.n         0.418130   0.112878   3.704 0.000212 ***
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# (Dispersion parameter for binomial family taken to be 1)
# 
#     Null deviance: 10066.4  on 16521  degrees of freedom
# Residual deviance:  9567.8  on 16509  degrees of freedom
# AIC: 9593.8
# 
# Number of Fisher Scoring iterations: 6


##getting predicted use as a function of zmax, at average zq60 and zcv
range.hmax <- range(var1$hmax)
range.hmax
#[1] 0.00 99.77

plotting_dfm <- expand.grid(hmax = seq(from = 0, to = 99.7, by = 10),
                            Species    = c("M.brandtii","M.mystacinus"),
                            D7 = mean(var1$D7),
                            gap3.sum.area = mean(var1$gap3.sum.area),
                            gap3.mean.area = mean(var1$gap3.mean.area),
                            gap5.mean.area = mean(var1$gap5.mean.area), 
                            gap5.n = mean(var1$gap5.n))

plotting_dfm$Species = as.factor(plotting_dfm$Species)

plotting_dfm$preds <- plogis( predict(fit.x , newdata=plotting_dfm))

 
##plotting the predicted response on the two covariates
windows()
pl <- ggplot(plotting_dfm, aes(x=hmax, y =preds, color=as.factor(Species)))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by hmax and Species") + 
  ggplot2::ylab("Predicted Use")


#----------------------------- gap5.n 

##getting predicted use as a function of zq60, at average zmax and zcv
range.gap5.n <- range(var1$gap5.n)
range.gap5.n
#[1] -0.6713285  5.7284651

plotting_dfm <- expand.grid(gap5.n = seq(from = -0.67, to = 5.73, by = 0.2),
                            Species    = c("M.brandtii","M.mystacinus"),
                            D7 = mean(var1$D7),
                            gap3.sum.area = mean(var1$gap3.sum.area),
                            gap3.mean.area = mean(var1$gap3.mean.area),
                            gap5.mean.area = mean(var1$gap5.mean.area), 
                            hmax = mean(var1$hmax))

plotting_dfm$Species = as.factor(plotting_dfm$Species)

plotting_dfm$preds <- plogis( predict(fit.x , newdata=plotting_dfm))


##plotting the predicted response on the two covariates
windows()
pl <- ggplot(plotting_dfm, aes(x=gap5.n, y =preds, color=as.factor(Species)))
pl + 
  geom_point( ) +
  geom_smooth() + 
  ggtitle("Predicted Use by gap5.n and Species") + 
  ggplot2::ylab("Predicted Use")








```

