---
title: "RSF"
output: html_document
date: "2023-10-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Prepare the workspace 
```{r}

### Prepare the work space
library(tidyverse)
library(dplyr)
library(scales)
library(beepr)
library(lubridate)
library(ResourceSelection)
library(RColorBrewer)
library(cowplot)
library(colorBlindness)
library(kableExtra)
library(lme4)
library(stats)
library(DHARMa)
library(lattice)
library(broom)
library(modelsummary)
library(kableExtra)
library(gt)
library(readxl)
library(xlsx)
library(corrplot)
library(vegan)
library(sjPlot)
library(car)
library(margins)


getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/Documents/1. PhD_Main/GitHub_link/Nittedal/SpatialAndMorphology_MBRA_MMYS"

output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs"

file.name <- "RSF"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today


```


# Import the dataset 
```{r}

## Covariates from LiDAR data prepared by Hans Ole 
vars <- readRDS("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Inputs/SpatialData/vars_dist45_v3.rds")

summary(vars)
str(vars) # sf data frame
# 16522 observations of 47 variables 

names(vars)
## For writing descriptions of each variable 

#mettext <- as.data.frame(names(vars))
# write.csv(mettext, "~mettext.csv") # 15.11.2023
```


# Housekeeping of LiDAR data 
```{r}
str(vars)
summary(vars)


# Hans Ole: HOW TO DEAL WITH NAs:
dt <- vars
summary(dt[is.na(dt$Hmean),])
dt$H10[is.na(dt$Hmax)] <- 0.5
dt$Hmean[is.na(dt$Hmean)] <- 0.5
dt$H10[is.na(dt$H10)] <- 0.5
dt$H20[is.na(dt$H20)] <- 0.5
dt$H30[is.na(dt$H30)] <- 0.5
dt$H40[is.na(dt$H40)] <- 0.5
dt$H50[is.na(dt$H50)] <- 0.5
dt$H60[is.na(dt$H60)] <- 0.5
dt$H70[is.na(dt$H70)] <- 0.5
dt$H80[is.na(dt$H80)] <- 0.5
dt$H90[is.na(dt$H90)] <- 0.5
dt$H95[is.na(dt$H95)] <- 0.5
set.seed(123)
un <- runif(10000)

dt$Hsd[is.na(dt$Hsd)] <- sd(un)
dt$Hcv[is.na(dt$Hcv)] <- dt$Hsd[is.na(dt$Hcv)] / dt$Hmean[is.na(dt$Hcv)]
dt$crown.mean.size[is.na(dt$crown.mean.size)] <- 0
dt$ttops.mean.height[is.na(dt$ttops.mean.height)] <- 0

dt$gap5.sd.area[is.na(dt$gap5.sd.area)] <- 0
dt$gap3.sd.area[is.na(dt$gap3.sd.area)] <- 0
dt$crown.sd.size[is.na(dt$crown.sd.size)] <- 0
dt$ttops.sd.height[is.na(dt$ttops.sd.height)] <- 0
summary(dt)

# Hmax -Inf = 0.5
dt$Hmax[dt$Hmax == "-Inf"] <- 0.5

## NAs for Hkurt and Hskewness: 
#  Generate a uniform distribution between 0 and 1 and compute the value of that

# Hkurt NA = -1.183527 
dt$Hkurt[is.na(dt$Hkurt)] <- -1.183527 

# Hskewness NA = 0.004507174 
dt$Hskewness[is.na(dt$Hskewness)] <- -0.004507174 


dt$Species=as.factor(dt$Species)
dt$BatID=as.factor(dt$BatID)
dt$water.objtype=as.factor(dt$water.objtype)

dt$YOD[is.na(dt$YOD)] <- "Undetected"
dt$YOD=as.factor(dt$YOD)


### Check for suspicious outliers
summary(dt)

# 16484 obs of 23 vars 
# There is an Hmax value of 99.77 m with the next highest value being ~30 m. This is some sort of miscalculation in the canopy height model, so it will be removed. (Available (used = 0) point for Astrid (MBRA)). 

## First convert to a normal dataframe(drop geoms/sf objects) 
dt1df <- as.data.frame(dt)
dt1df <- dt1df %>% select(-geom)
# 16484 obs of 49 vars

dt2df <- dt1df %>% dplyr::filter(Hmax < 90)
# 16483 obs of 49 vars

#### Scale continuous variables for ordination and modelling
dt1 <- dt2df # Use this to scale all continuous numerical data 
dt1[,7:46]=scale(dt1[,7:46], scale=TRUE) #
#
# names(dt1)

```

## Data exploration - raw data (unscaled)
```{r}
# summary(dt2df)
# 
# ## Are there any strong outliers amongst n of local maxima? 
# hist(dt2df$ttops.n) 
# 
# # How does this look for used points? 
# dt2dfused <- dt2df %>% filter(used == 1)
# hist(dt2dfused$ttops.n) 
# # what proportion of the dataset has a ttops.n value of less than 5? 
#  
# openareas <- dt2df %>% filter(ttops.n <= 5)
# # 2377 obs 
# 2377/16483
# # 14%
# # How many of these open area observations are actual used points? 
# 
# summary(openareas)
# table(openareas$used) # 17 points 
#  
# openused <- openareas %>% filter(used == 1 ) %>%  droplevels()
# 
# summary(openused)
# table(openused$Species)
#   # M.brandtii M.mystacinus 
#   #          8            9 
# table(openused$BatID)
# # Amelia  Dagny  Ethel Louise Phoebe  Reeda Steffi  Stine   Thea 
# #      2      1      2      2      5      1      1      2      1 
# 
# ### Think of a way to more distinctly categorize "open areas". 

```



## Correlation/collinearity between LiDAR variables 
```{r}
# names(dt1)
# dtc <- dt1 %>% dplyr::select(c(
#   Hmax, Hmean, Hsd, Hcv, Hskewness, 
#   H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
#   D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
#   gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
#   gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
#   ttops.n, ttops.mean.height, ttops.sd.height)) 
# 
# windows()
# 
# corrplot(cor(dtc))
```



# NMDS ordination of available points to address collinearity and discern patterns in how variables influence each other 


### Prepare data for PCA 
```{r}

## Create an ID column so the bat meta data can be reattached later

## Create a unique row id which will become "idvar"

dt1$idvar <- paste0("ID-", 1:nrow(dt1)) 
headings <- dt1$idvar

## Now only includeLiDAR variables with IDvar
names(dt1)

dt2 <- dt1 %>% dplyr::select(c(
  Hmax, Hmean, Hsd, Hcv, Hskewness, Hkurt, 
  H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
  D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
  gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
  gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
  ttops.n, ttops.mean.height, ttops.sd.height)) 
## Remove hskewness for now because it has negative values... 
rownames(dt2) <- headings
# Reshape into wide format 

summary(dt2)
## This is a PCA, more info below: 

mat <- dt2 

```


## Principal component analysis 
Resources: 
https://www.flutterbys.com.au/stats/tut/tut14.2.html

```{r}
## PCA 
trait.pca <- rda(mat) # used and available points together 

biplot(trait.pca) 
# simple plot 
screeplot(trait.pca) 
# how much of each axis describes the variation in the data 
# PC1 Explains most of the variation. Big difference between PC2 and PC3. 

summary(trait.pca)

pca.summary <- summary(trait.pca)

## In our case, 'species' are the different LiDAR variables and sites are the different bat locations. 
trait.loadings <- as.data.frame(pca.summary$species) %>% 
  mutate(trait = rownames(.))  
head(trait.loadings)

meta <- dt1 %>% dplyr::select(c(used, Species, idvar)) 
# for now, do not include bat.id

## Build meta data to be reattached in plotting
rownames(meta) <- meta$idvar
meta$gen.spe <- meta$idvar
meta$used <- as.factor(meta$used)

# Scores for all the different bat locations 
sp.scores <- as.data.frame(pca.summary$sites) %>% 
  mutate(gen.spe = rownames(.)) %>% inner_join(meta) 
# 

traittable <- trait.loadings  %>% 
  dplyr::select(trait, PC1, PC2)
#write.csv(traittable, file = file.path(output_today, "bothbats_allpts_PCA1_2_table.csv")) # 26.11.2023

### Compare trait loadings for bat locations with Pearson's correlation of PC1 and PC2, as well as of the LiDAR variables with each other 
spdf <- left_join(sp.scores, dt1, by = "idvar")
spdf1 <- spdf %>% dplyr::select(-c(PC3, PC4, PC5, PC6, idvar, gen.spe, used.x, used.y, Species.x, Species.y, BatID, Easting, Northing, UTM, YOD, DIST, water.distance, water.objtype))


#corrplot(cor(dtc))
cortab <- as.data.frame(cor(spdf1)) 

windows()
corrplot(cor(spdf1),
         tl.col="black", tl.srt=45,  
         type="lower", col=brewer.pal(n=5, name="Greys"))

cortab1 <- cortab[1:2,]
cortab2 <- t(cortab1) # Table of the values for further comparing 

#write.csv(cortab2, file = file.path(output_today, "cortab2.csv"))
# 28.11.2023

################################################################################
##### plotting 
################################################################################

## PC1 and PC2
pca.ggplot <- ggplot(data = sp.scores, aes(x = PC1, y = PC2)) +
  geom_point() +
  geom_segment(data = trait.loadings, 
               aes(x = 0, xend = PC1/2, y = 0, yend = PC2/2), lwd = 0.1) + 
  geom_text(data = trait.loadings, aes(x = PC1/2, y = PC2/2+0.1, label = trait), size = 3) + 
  theme_bw() 
pca.ggplot ## Use this for grouping variables 

## PC1 and PC3
pca.ggplot <- ggplot(data = sp.scores, aes(x = PC1, y = PC3)) +
  geom_point() +
  geom_segment(data = trait.loadings, 
               aes(x = 0, xend = PC1/2, y = 0, yend = PC2/2), lwd = 0.1) + 
  geom_text(data = trait.loadings, aes(x = PC1/2, y = PC2/2+0.1, label = trait), size = 3) + 
  theme_bw() 
pca.ggplot

```


# Model selection (explortatory approach)
We determined that the following covariates can be used to describe most of the variation in the LiDAR variables based on comparing the ordination of all LiDAR variables with PC1 and PC2, trait loadings and pearsons correlations coefficients between covariates and PC1:

H95
gap.sum.area (3 and 5)
gap.sd.area (3 and 5)
D0
Hsd

In addition we will include distance to water (dist.water) and bat ID as a random effect. 

I begin by modelling for each bat species separately with two candidate models - one with gap varaibles at 3 m and another with gap variables at 5 m. 

## RSF
```{r}

## Simple models - separated by bat species, no species interaction 
# install.packages("lme4", type = "source") 
# library(lme4)


MBRA <- dt1 %>% filter(Species == "M.brandtii") %>% droplevels() # 7633 obs of 49 vars
MMYS <- dt1 %>% filter(Species == "M.mystacinus") %>% droplevels() # 8850 obs of 49 vars

########################################################
########################  MBRA  ########################
########################################################

fit1MBRA= glmer(used ~  
                  gap3.mean.area + gap3.sd.area +
                  D0 + H95 + Hsd + water.distance +
                  (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

fit2MBRA= glmer(used ~  
                  gap5.mean.area + gap5.sd.area +
                  D0 + H95 + Hsd + water.distance +
                  (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')

isSingular(fit1MBRA)
# FALSE

isSingular(fit2MBRA)
# TRUE

AIC(fit1MBRA, fit2MBRA)
#          df      AIC
# fit1MBRA  8 4367.075
# fit2MBRA  8 4330.863 # fit 2 has a lower AIC weight BUT it gets flagged for having a singular fit so I would instead want to use the model with the 3 m resolution gap variables. 

########################################################
########################  MMYS  ########################
########################################################

fit1MMYS= glmer(used ~  
                  gap3.mean.area + gap3.sd.area +
                  D0 + H95 + Hsd + water.distance +
                  (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

fit2MMYS= glmer(used ~  
                  gap5.mean.area + gap5.sd.area +
                  D0 + H95 + Hsd + water.distance +
                  (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

AIC(fit1MMYS, fit2MMYS)
#          df      AIC
# fit1MMYS  8 5114.563
# fit2MMYS  8 5114.292 # The difference between the weights is negligible, I feel comfortable sticking with the 3 m resolution due to the singularity issues found in the M. brandtii models. 

################################################
# The gap5 model for MBRA throws a singularity warning, and the AIC weights between the model pairs is very little so I will use the 3 m resolution models to continue. 

summary(fit1MBRA)
# Generalized linear mixed model fit by maximum likelihood (Adaptive
#   Gauss-Hermite Quadrature, nAGQ = 0) [glmerMod]
#  Family: binomial  ( logit )
# Formula: 
# used ~ gap3.mean.area + gap3.sd.area + D0 + H95 + Hsd + water.distance +  
#     (1 | BatID)
#    Data: MBRA
# 
#      AIC      BIC   logLik deviance df.resid 
#   4367.1   4422.6  -2175.5   4351.1     7625 
# 
# Scaled residuals: 
#     Min      1Q  Median      3Q     Max 
# -0.8595 -0.3602 -0.2616 -0.1916  6.3952 
# 
# Random effects:
#  Groups Name        Variance Std.Dev.
#  BatID  (Intercept) 0.003437 0.05863 
# Number of obs: 7633, groups:  BatID, 10
# 
# Fixed effects:
#                Estimate Std. Error z value Pr(>|z|)    
# (Intercept)    -2.41283    0.04967 -48.579  < 2e-16 ***
# gap3.mean.area -0.29348    0.06880  -4.265 2.00e-05 ***
# gap3.sd.area   -0.08817    0.04445  -1.984   0.0473 *  
# D0             -0.32482    0.06326  -5.135 2.83e-07 ***
# H95             0.74449    0.11199   6.648 2.97e-11 ***
# Hsd            -0.22818    0.10099  -2.259   0.0239 *  
# water.distance -0.44822    0.05015  -8.937  < 2e-16 ***
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Correlation of Fixed Effects:
#             (Intr) gp3.m. gp3.s. D0     H95    Hsd   
# gap3.mean.r  0.012                                   
# gap3.sd.are -0.060  0.438                            
# D0           0.108  0.518  0.456                     
# H95         -0.161  0.300  0.119 -0.229              
# Hsd          0.044 -0.122 -0.136  0.232 -0.878       
# water.dstnc  0.189  0.255  0.207  0.005  0.019  0.051


summary(fit1MMYS)
# Generalized linear mixed model fit by maximum likelihood (Adaptive
#   Gauss-Hermite Quadrature, nAGQ = 0) [glmerMod]
#  Family: binomial  ( logit )
# Formula: 
# used ~ gap3.mean.area + gap3.sd.area + D0 + H95 + Hsd + water.distance +  
#     (1 | BatID)
#    Data: MMYS
# 
#      AIC      BIC   logLik deviance df.resid 
#   5114.6   5171.3  -2549.3   5098.6     8842 
# 
# Scaled residuals: 
#     Min      1Q  Median      3Q     Max 
# -0.9268 -0.3587 -0.2780 -0.1950  9.3631 
# 
# Random effects:
#  Groups Name        Variance Std.Dev.
#  BatID  (Intercept) 0.02742  0.1656  
# Number of obs: 8850, groups:  BatID, 11
# 
# Fixed effects:
#                Estimate Std. Error z value Pr(>|z|)    
# (Intercept)    -2.58026    0.07143 -36.124  < 2e-16 ***
# gap3.mean.area  0.18598    0.07071   2.630 0.008533 ** 
# gap3.sd.area    0.13158    0.04653   2.828 0.004686 ** 
# D0              0.26618    0.06871   3.874 0.000107 ***
# H95             0.66503    0.12364   5.379 7.49e-08 ***
# Hsd             0.03934    0.09400   0.419 0.675573    
# water.distance -0.48758    0.05212  -9.356  < 2e-16 ***
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Correlation of Fixed Effects:
#             (Intr) gp3.m. gp3.s. D0     H95    Hsd   
# gap3.mean.r  0.036                                   
# gap3.sd.are  0.019  0.283                            
# D0          -0.020  0.426  0.445                     
# H95         -0.159  0.242 -0.009 -0.455              
# Hsd          0.031 -0.028 -0.047  0.450 -0.849       
# water.dstnc  0.231  0.141  0.074 -0.253  0.119 -0.065


sjPlot::tab_model(fit1MBRA, fit1MMYS,fit2MBRA, fit2MMYS,
                  dv.labels = c(
                    "Myotis brandtii - 3 m", "Myotis mystacinus - 3 m",
                    "Myotis brandtii - 5 m", "Myotis mystacinus - 5 m"), transform = NULL, auto.label = FALSE) 

```

## Model diagnostics 
fit1MBRA
fit1MMYS

```{r}

### Diagnostics for fit1MBRA 
simulationOutput <- simulateResiduals(fittedModel = fit1MBRA, plot = T)
### Help with interpretation of residuals vs. predicted: 
# https://stats.stackexchange.com/questions/449208/diagnostic-plot-residual-vs-predicted-of-a-glmm-using-dharma
### recalculateResiduals()

# KS test -  the p-value shows you that there is *not* a significant deviation from the assumed distribution
# Dispersion test – Not over or underdispersed
# Outlier – No indication of outliers 
# 
# Residuals appear to more or less agree with predicted values 



windows()
testDispersion(simulationOutput)
# 
# 	DHARMa nonparametric dispersion test via sd of residuals fitted vs.
# 	simulated
# 
# data:  simulationOutput
# dispersion = 1.005, p-value = 0.888
# alternative hypothesis: two.sided



testZeroInflation(simulationOutput)
# 	DHARMa zero-inflation test via comparison to expected zeros with simulation
# 	under H0 = fitted model
# 
# data:  simulationOutput
# ratioObsSim = 0.99996, p-value = 0.992
# alternative hypothesis: two.sided

testQuantiles(simulationOutput)
# 	Test for location of quantiles via qgam
# 
# data:  simulationOutput
# p-value = 0.08098
# alternative hypothesis: both

testCategorical(simulationOutput, catPred = MBRA$BatID)
## No bat IDs had a low p value for the Asymptotic  one-sample Kolmogorov-Smirnov test

levels(MMYS$BatID)



##########################################################################

### Diagnostics for fit1MMYS 
simulationOutput <- simulateResiduals(fittedModel = fit1MMYS, plot = T)


### Help with interpretation of residuals vs. predicted: 
# https://stats.stackexchange.com/questions/449208/diagnostic-plot-residual-vs-predicted-of-a-glmm-using-dharma
### recalculateResiduals()

# KS test -  the p-value shows you that there is *not* a significant deviation from the assumed distribution
# Dispersion test – Not over or underdispersed
# Outlier – No indication of outliers 
# 
# Residuals appear to more or less agree with predicted values 



windows()
testDispersion(simulationOutput)
# 
# 	DHARMa nonparametric dispersion test via sd of residuals fitted vs.
# 	simulated
# 
# data:  simulationOutput
# dispersion = 1.005, p-value = 0.888
# alternative hypothesis: two.sided
# No evidence of dispersion 



testZeroInflation(simulationOutput)
# 	DHARMa zero-inflation test via comparison to expected zeros with simulation
# 	under H0 = fitted model
# 
# data:  simulationOutput
# ratioObsSim = 1.0025, p-value = 0.64
# alternative hypothesis: two.sided

testQuantiles(simulationOutput)
# 	Test for location of quantiles via qgam
# 
# data:  simulationOutput
# p-value = 0.0005186
# alternative hypothesis: both



testCategorical(simulationOutput, catPred = MMYS$BatID)
## No bat IDs had a low p value for the Asymptotic  one-sample Kolmogorov-Smirnov test

```


## Sketch model fit for model  to understand what the model is telling us 
```{r}
############################################################

##refitting model with GLM to sketch results

fit1mbra <- glm(used ~ gap3.mean.area + gap3.sd.area +
                  D0 + H95 + Hsd + water.distance,
                  family=binomial(), data=MBRA)

summary(fit1mbra)
# Call:
# glm(formula = used ~ gap3.mean.area + gap3.sd.area + D0 + H95 + 
#     Hsd + water.distance, family = binomial(), data = MBRA)
# 
# Coefficients:
#                Estimate Std. Error z value Pr(>|z|)    
# (Intercept)    -2.40805    0.04526 -53.209  < 2e-16 ***
# gap3.mean.area -0.30531    0.06786  -4.499 6.82e-06 ***
# gap3.sd.area   -0.09343    0.04414  -2.116   0.0343 *  
# D0             -0.32678    0.06311  -5.178 2.24e-07 ***
# H95             0.74136    0.11152   6.648 2.98e-11 ***
# Hsd            -0.23026    0.10086  -2.283   0.0224 *  
# water.distance -0.44066    0.04958  -8.888  < 2e-16 ***
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# (Dispersion parameter for binomial family taken to be 1)
# 
#     Null deviance: 4651.0  on 7632  degrees of freedom
# Residual deviance: 4351.3  on 7626  degrees of freedom
# AIC: 4365.3
# 
# Number of Fisher Scoring iterations: 5



#----------------------------- gap3.mean
##getting predicted use 
range.gapmean <- range(MBRA$gap3.mean.area)
range.gapmean
# -0.7824953  1.5548690

mbra.plotting_dfm <- expand.grid(
  H95 = mean(MBRA$H95),
  D0 = mean(MBRA$D0),
  gap3.mean.area = seq(from = -0.7824953, to = 1.5548690, by = 0.3),
  gap3.sd.area = mean(MBRA$gap3.sd.area),
  Hsd = mean(MBRA$Hsd), 
  water.distance = mean(MBRA$water.distance)) 


mbra.plotting_dfm$preds <- plogis( predict(fit1mbra , newdata=mbra.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mbra.plotting_dfm, aes(x=gap3.mean.area, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by gap3.mean.area for Myotis brandtii") + 
  ggplot2::ylab("Predicted Use")



#----------------------------- gap3.SD
##getting predicted use 
range.gapsd <- range(MBRA$gap3.sd.area)
range.gapsd
# -0.6537116  3.1228513

mbra.plotting_dfm <- expand.grid(
  H95 = mean(MBRA$H95),
  D0 = mean(MBRA$D0),
  gap3.mean.area = mean(MBRA$gap3.mean.area),
  gap3.sd.area = seq(from = -0.6537116, to = 3.1228513, by = 0.3),
  Hsd = mean(MBRA$Hsd), 
  water.distance = mean(MBRA$water.distance)) 


mbra.plotting_dfm$preds <- plogis( predict(fit1mbra , newdata=mbra.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mbra.plotting_dfm, aes(x=gap3.sd.area, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by gap3.sd.area for Myotis brandtii") + 
  ggplot2::ylab("Predicted Use")

#----------------------------- D0
##getting predicted use 
range.D0 <- range(MBRA$D0)
range.D0
# -1.059072  2.854221

mbra.plotting_dfm <- expand.grid(
  H95 = mean(MBRA$H95),
  D0 = seq(from = -1.059072  , to = 2.854221, by = 0.3),
  gap3.mean.area = mean(MBRA$gap3.mean.area),
  gap3.sd.area = mean(MBRA$gap3.sd.area),
  Hsd = mean(MBRA$Hsd), 
  water.distance = mean(MBRA$water.distance)) 


mbra.plotting_dfm$preds <- plogis( predict(fit1mbra , newdata=mbra.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mbra.plotting_dfm, aes(x=D0, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by D0 for Myotis brandtii") + 
  ggplot2::ylab("Predicted Use")

#----------------------------- Hsd
##getting predicted use 
range.Hsd <- range(MBRA$Hsd)
range.Hsd
# -2.125363  3.625778

mbra.plotting_dfm <- expand.grid(
  H95 = mean(MBRA$H95),
  D0 = mean(MBRA$D0),
  gap3.mean.area = mean(MBRA$gap3.mean.area),
  gap3.sd.area = mean(MBRA$gap3.sd.area),
  Hsd = seq(from = -2.125363  , to = 3.625778, by = 0.5), 
  water.distance = mean(MBRA$water.distance)) 


mbra.plotting_dfm$preds <- plogis( predict(fit1mbra , newdata=mbra.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mbra.plotting_dfm, aes(x=Hsd, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by Hsd for Myotis brandtii") + 
  ggplot2::ylab("Predicted Use")

#----------------------------- distance to water
##getting predicted use 
range.water.distance <- range(MBRA$water.distance)
range.water.distance
# -1.194830  3.878212

mbra.plotting_dfm <- expand.grid(
  H95 = mean(MBRA$H95),
  D0 = mean(MBRA$D0),
  gap3.mean.area = mean(MBRA$gap3.mean.area),
  gap3.sd.area = mean(MBRA$gap3.sd.area),
  Hsd = mean(MBRA$Hsd), 
  water.distance = seq(from = -1.194830  , to = 3.878212, by = 0.3)) 


mbra.plotting_dfm$preds <- plogis( predict(fit1mbra , newdata=mbra.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mbra.plotting_dfm, aes(x=water.distance, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by distance to water for Myotis brandtii") + 
  ggplot2::ylab("Predicted Use")



```



# Now re-fit the models with a GLM to sketch prediction plots 


```{r}
######## MMYS ###########

## Refitting the model with GLM to sketch results

fit1mmys<- glm(used ~ gap3.mean.area + gap3.sd.area +
                  D0 + H95 + Hsd + water.distance,
                  family=binomial(), data=MMYS)

summary(fit1mmys)
# Call:
# glm(formula = used ~ gap3.mean.area + gap3.sd.area + D0 + H95 + 
#     Hsd + water.distance, family = binomial(), data = MMYS)
# 
# Coefficients:
#                Estimate Std. Error z value Pr(>|z|)    
# (Intercept)    -2.56789    0.04748 -54.078  < 2e-16 ***
# gap3.mean.area  0.19242    0.06987   2.754 0.005889 ** 
# gap3.sd.area    0.13277    0.04628   2.869 0.004120 ** 
# D0              0.23425    0.06697   3.498 0.000469 ***
# H95             0.64274    0.11774   5.459 4.79e-08 ***
# Hsd             0.04368    0.09033   0.483 0.628755    
# water.distance -0.45563    0.05110  -8.916  < 2e-16 ***
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# (Dispersion parameter for binomial family taken to be 1)
# 
#     Null deviance: 5408.0  on 8849  degrees of freedom
# Residual deviance: 5104.5  on 8843  degrees of freedom
# AIC: 5118.5
# 
# Number of Fisher Scoring iterations: 6


##getting predicted use as a function of zmax, at average zq60 and zcv
range.h95 <- range(MMYS$H95)
range.h95
# -2.174677  2.221490

mmys.plotting_dfm <- expand.grid(
  H95 = seq(from = -2.174677, to = 2.187593, by = 0.5),
  D0 = mean(MMYS$D0),
  gap3.sd.area = mean(MMYS$gap3.sd.area),
  gap3.mean.area = mean(MMYS$gap3.mean.area),
  Hsd = mean(MMYS$Hsd), 
  water.distance = mean(MMYS$water.distance)) 


mmys.plotting_dfm$preds <- plogis( predict(fit1mmys , newdata=mmys.plotting_dfm))

 
## plotting the predicted response on the two covariates
# windows()
pl <- ggplot(mmys.plotting_dfm, aes(x=H95, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by H95 for Myotis mystacinus") + 
  ggplot2::ylab("Predicted Use")


#----------------------------- gap3.mean
##getting predicted use 
range.gapmean <- range(MMYS$gap3.mean.area)
range.gapmean
# -0.782728  1.554869

mmys.plotting_dfm <- expand.grid(
  H95 = mean(MMYS$H95),
  D0 = mean(MMYS$D0),
  gap3.mean.area = seq(from = -0.782728, to = 1.554869, by = 0.3),
  gap3.sd.area = mean(MMYS$gap3.sd.area),
  Hsd = mean(MMYS$Hsd), 
  water.distance = mean(MMYS$water.distance)) 


mmys.plotting_dfm$preds <- plogis( predict(fit1mmys , newdata=mmys.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mmys.plotting_dfm, aes(x=gap3.mean.area, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by gap3.mean.area for Myotis mystacinus") + 
  ggplot2::ylab("Predicted Use")


#----------------------------- gap3.SD
##getting predicted use 
range.gapsd <- range(MMYS$gap3.sd.area)
range.gapsd
# -0.6537116  3.1268099

mmys.plotting_dfm <- expand.grid(
  H95 = mean(MMYS$H95),
  D0 = mean(MMYS$D0),
  gap3.mean.area = mean(MMYS$gap3.mean.area),
  gap3.sd.area = seq(from = -0.6537116, to = 3.1268099, by = 0.3),
  Hsd = mean(MMYS$Hsd), 
  water.distance = mean(MMYS$water.distance)) 


mmys.plotting_dfm$preds <- plogis( predict(fit1mmys , newdata=mmys.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mmys.plotting_dfm, aes(x=gap3.sd.area, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by gap3.sd.area for Myotis mystacinus") + 
  ggplot2::ylab("Predicted Use")


#----------------------------- D0
##getting predicted use 
range.D0 <- range(MMYS$D0)
range.D0
# -1.059072  2.854221

mmys.plotting_dfm <- expand.grid(
  H95 = mean(MMYS$H95),
  D0 = seq(from = -1.059072, to = 2.854221, by = 0.3),
  gap3.mean.area = mean(MMYS$gap3.mean.area),
  gap3.sd.area = mean(MMYS$gap3.sd.area),
  Hsd = mean(MMYS$Hsd), 
  water.distance = mean(MMYS$water.distance)) 


mmys.plotting_dfm$preds <- plogis( predict(fit1mmys , newdata=mmys.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mmys.plotting_dfm, aes(x=D0, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by D0 for Myotis mystacinus") + 
  ggplot2::ylab("Predicted Use")

#----------------------------- Hsd
##getting predicted use 
range.Hsd <- range(MMYS$Hsd)
range.Hsd
# -2.118514  2.845969

mmys.plotting_dfm <- expand.grid(
  H95 = mean(MMYS$H95),
  D0 = mean(MMYS$D0),
  gap3.mean.area = mean(MMYS$gap3.mean.area),
  gap3.sd.area = mean(MMYS$gap3.sd.area),
  Hsd = seq(from = -2.118514  , to = 2.845969, by = 0.3), 
  water.distance = mean(MMYS$water.distance)) 


mmys.plotting_dfm$preds <- plogis( predict(fit1mmys , newdata=mmys.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mmys.plotting_dfm, aes(x=Hsd, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by Hsd for Myotis mystacinus") + 
  ggplot2::ylab("Predicted Use")


#----------------------------- distance to water
##getting predicted use 
range.water.distance <- range(MMYS$water.distance)
range.water.distance
# -1.194830  3.682869

mmys.plotting_dfm <- expand.grid(
  H95 = mean(MMYS$H95),
  D0 = mean(MMYS$D0),
  gap3.mean.area = mean(MMYS$gap3.mean.area),
  gap3.sd.area = mean(MMYS$gap3.sd.area),
  Hsd = mean(MMYS$Hsd), 
  water.distance = seq(from = -1.194830  , to = 3.682869, by = 0.3)) 


mmys.plotting_dfm$preds <- plogis( predict(fit1mmys , newdata=mmys.plotting_dfm))

 
##plotting the predicted response on the two covariates
#windows()
pl <- ggplot(mmys.plotting_dfm, aes(x=water.distance, y =preds))
pl + 
  geom_point() +
  geom_smooth() + 
  ggtitle("Predicted Use by distance to water for Myotis mystacinus") + 
  ggplot2::ylab("Predicted Use")


```


## Use the VIF function to test for correlation amongst variables 

```{r}

### VIF equal to 1 = variables are not correlated.
## VIF between 1 and 5 = variables are moderately correlated.
## VIF greater than 5 = variables are highly correlated2.

vif(fit1MBRA)
# gap3.mean.area   gap3.sd.area             D0            H95 
#       2.348361       1.499023       2.131783       6.173876 
#            Hsd water.distance 
#       5.198530       1.170715 

vif(fit1MMYS)
      # 2.173564       1.469705       3.080542       5.478972 
      #      Hsd water.distance 
      # 4.285148       1.279439

# Drop Hsd to see how this changes the correlation amongst variables 

fit3MBRA= glmer(used ~  
                  gap3.mean.area + gap3.sd.area +
                  D0 + H95 + water.distance +
                  (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

fit3MMYS= glmer(used ~  
                  gap3.mean.area + gap3.sd.area +
                  D0 + H95 + water.distance +
                  (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

vif(fit3MBRA)
# gap3.mean.area   gap3.sd.area             D0            H95 water.distance 
#       2.314458       1.474632       2.016042       1.396957       1.162424 

vif(fit3MMYS)
# gap3.mean.area   gap3.sd.area             D0            H95 water.distance 
#       2.166326       1.465539       2.453237       1.533037       1.273023 

## Correlation between variables no longer so severe, but H95 appears to have a similar influence to gap3.mean in the ordination and H95 also had higher VIF values than Hsd so it is wiser to remove H95 and keep Hsd so long as doing so also reduces the correlation issues amongst variables. 

fit4MBRA= glmer(used ~  
                  gap3.mean.area + gap3.sd.area +
                  D0 + Hsd + water.distance +
                  (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 

fit4MMYS= glmer(used ~  
                  gap3.mean.area + gap3.sd.area +
                  D0 + Hsd + water.distance +
                  (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 

vif(fit4MBRA)
# gap3.mean.area   gap3.sd.area             D0            Hsd water.distance 
#       2.181516       1.475660       2.037141       1.197588       1.161518 
vif(fit4MMYS)
# gap3.mean.area   gap3.sd.area             D0            Hsd water.distance 
#       2.137838       1.454669       2.463226       1.242854       1.268480 

## Correlation between variables no longer so severe, use this group of variables to create a more complex model with both bat species - species will then need to interact with each environmental variable. 

bigfit1 = glmer(used ~  Species + 
                  gap3.mean.area + gap3.sd.area +
                  D0 + Hsd + water.distance +
                  Species*gap3.mean.area + 
                  Species*gap3.sd.area +
                  Species*D0 + 
                  Species*Hsd + 
                  Species*water.distance +
                  (1|BatID), data=dt1,
              family=binomial(link="logit"),nAGQ = 0)

summary(bigfit1)

## Now step-wise selection with AIC 
drop1(bigfit1)

# used ~ Species + gap3.mean.area + gap3.sd.area + D0 + Hsd + water.distance + 
#     Species * gap3.mean.area + Species * gap3.sd.area + Species * 
#     D0 + Species * Hsd + Species * water.distance + (1 | BatID)
#                        npar    AIC
# <none>                      9547.5
# Species:gap3.mean.area    1 9572.7
# Species:gap3.sd.area      1 9559.7
# Species:D0                1 9601.4
# Species:Hsd               1 9547.9
# Species:water.distance    1 9545.9 *** # Suggests to drop water.distance*Species 
  
bigfit2 =  glmer(used ~  Species + 
                   gap3.mean.area + gap3.sd.area +
                   D0 + Hsd + water.distance +
                   Species*gap3.mean.area + 
                   Species*gap3.sd.area +
                   Species*D0 + 
                   Species*Hsd + 
                   (1|BatID), data=dt1,
               family=binomial(link="logit"),nAGQ = 0)

summary(bigfit2)
#      AIC      BIC   logLik deviance df.resid 
#   9545.9   9638.4  -4760.9   9521.9    16471 
# 
# Scaled residuals: 
#     Min      1Q  Median      3Q     Max 
# -0.8166 -0.3549 -0.2744 -0.2027  7.9794 
# 
# Random effects:
#  Groups Name        Variance Std.Dev.
#  BatID  (Intercept) 0.0154   0.1241  
# Number of obs: 16483, groups:  BatID, 21
# 
# Fixed effects:
#                                    Estimate Std. Error z value Pr(>|z|)    
# (Intercept)                        -2.39749    0.06093 -39.348  < 2e-16 ***
# SpeciesM.mystacinus                -0.13301    0.08436  -1.577 0.114871    
# gap3.mean.area                     -0.41836    0.06645  -6.296 3.06e-10 ***
# gap3.sd.area                       -0.11523    0.04470  -2.578 0.009946 ** 
# D0                                 -0.22709    0.06265  -3.625 0.000289 ***
# Hsd                                 0.36498    0.04728   7.719 1.17e-14 ***
# water.distance                     -0.49016    0.03594 -13.639  < 2e-16 ***
# SpeciesM.mystacinus:gap3.mean.area  0.51983    0.09551   5.443 5.25e-08 ***
# SpeciesM.mystacinus:gap3.sd.area    0.25065    0.06415   3.907 9.34e-05 ***
# SpeciesM.mystacinus:D0              0.64693    0.08739   7.403 1.33e-13 ***
# SpeciesM.mystacinus:Hsd             0.11124    0.06783   1.640 0.101011    
sjPlot::tab_model(bigfit2, transform = NULL, auto.label = FALSE) 

drop1(bigfit2)
# boundary (singular) fit: see help('isSingular')
## Suggests to keep everything 
#                        npar    AIC
# <none>                      9545.9 # Do not drop any further 
# water.distance            1 9746.2
# Species:gap3.mean.area    1 9572.8
# Species:gap3.sd.area      1 9558.9
# Species:D0                1 9599.5
# Species:Hsd               1 9546.6

## Make predictions from bigfit2

## Multi pannel graph 
# 4 LiDAR variables (x) 
# Probability of use (y) 
# Plot the predictions with two lines - one for each bat species 
```

## First, model diagnostics 
```{r}
### Diagnostics for fit1MBRA 
simulationOutput <- simulateResiduals(fittedModel = bigfit2, plot = T)
### Help with interpretation of residuals vs. predicted: 
# https://stats.stackexchange.com/questions/449208/diagnostic-plot-residual-vs-predicted-of-a-glmm-using-dharma
### recalculateResiduals()

# KS test -  the p-value shows you that there is *not* a significant deviation from the assumed distribution
# Dispersion test – Not over or underdispersed
# Outlier – No indication of outliers 
# 
# Residuals appear to more or less agree with predicted values 



#windows()
testDispersion(simulationOutput)
# 
# 	DHARMa nonparametric dispersion test via sd of residuals fitted vs.
# 	simulated
# 
# data:  simulationOutput
# dispersion = 0.9964, p-value = 0.944
# alternative hypothesis: two.sided

# no strong evidence for Dispersion issues 

testZeroInflation(simulationOutput)
# 	DHARMa zero-inflation test via comparison to expected zeros with simulation
# 	under H0 = fitted model
# 
# data:  simulationOutput
# ratioObsSim = 1.0012, p-value = 0.816
# alternative hypothesis: two.sided

# No strong evidence for zero inflation 

testQuantiles(simulationOutput)
# 	Test for location of quantiles via qgam
# 
# data:  simulationOutput
# p-value < 2.2e-16
# alternative hypothesis: both

## Evidence found that there are strong deviations from residuals and predicted values** 

# "A significant p-value for the splines means the fitted spline deviates from a flat line at the expected location (p-values of intercept and spline are combined via Benjamini & Hochberg adjustment to control the FDR)

#The p-values of the splines are combined into a total p-value via Benjamini & Hochberg adjustment to control the FDR."


testCategorical(simulationOutput, catPred = dt1$BatID)
## No bat IDs had a low p value for the Asymptotic  one-sample Kolmogorov-Smirnov test

testCategorical(simulationOutput, catPred = dt1$Species)
## No bat species had a low p value for the Asymptotic  one-sample Kolmogorov-Smirnov test

vif(bigfit2)
## Everything is under 5.0 or right at the border at least (D0) 
#                Species         gap3.mean.area           gap3.sd.area 
#               1.096853               4.120711               2.817547 
#                     D0                    Hsd         water.distance 
#               4.598903               2.371482               1.198596 
# Species:gap3.mean.area   Species:gap3.sd.area             Species:D0 
#               4.186560               2.785603               5.034330 
#            Species:Hsd 
#               2.506020 

```

## Plot predictions using glm 

```{r}

## Refitting the model with GLM to sketch results
bigfit2.0<- glm(used ~  Species + 
                   gap3.mean.area + gap3.sd.area +
                   D0 + Hsd + water.distance +
                   Species*gap3.mean.area + 
                   Species*gap3.sd.area +
                   Species*D0 + 
                   Species*Hsd, 
                  family=binomial(), data=dt1)

summary(bigfit2.0)
# Call:
# glm(formula = used ~ gap3.mean.area + gap3.sd.area + D0 + H95 + 
#     Hsd + water.distance, family = binomial(), data = MMYS)
# 
# Coefficients:
#                Estimate Std. Error z value Pr(>|z|)    
# (Intercept)    -2.56789    0.04748 -54.078  < 2e-16 ***
# gap3.mean.area  0.19242    0.06987   2.754 0.005889 ** 
# gap3.sd.area    0.13277    0.04628   2.869 0.004120 ** 
# D0              0.23425    0.06697   3.498 0.000469 ***
# H95             0.64274    0.11774   5.459 4.79e-08 ***
# Hsd             0.04368    0.09033   0.483 0.628755    
# water.distance -0.45563    0.05110  -8.916  < 2e-16 ***
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# (Dispersion parameter for binomial family taken to be 1)
# 
#     Null deviance: 5408.0  on 8849  degrees of freedom
# Residual deviance: 5104.5  on 8843  degrees of freedom
# AIC: 5118.5
# 
# Number of Fisher Scoring iterations: 6

batcolors = c("#32A5FF", "#011f4b") 

### Plotting predictions ####

# gap3.mean ---------------------------------------
range.gm <- range(dt1$gap3.mean.area)
range.gm
# -0.782728  1.554869
  
pred <- data.frame(expand.grid(
  D0 = mean(dt1$D0),
  gap3.sd.area = mean(dt1$gap3.sd.area),
  gap3.mean.area = seq(from = -0.782728  , to = 1.554869, by = 0.1),
  Hsd = mean(dt1$Hsd), 
  water.distance = mean(dt1$water.distance),
  Species = c("M.brandtii", "M.mystacinus"))) 
  
pred <- cbind(pred, predict(bigfit2.0, newdata = pred,
                             type = "link", se.fit = TRUE))

pred$PP <- plogis(pred$fit)
pred$LL <- plogis(pred$fit - (1.96 * pred$se.fit))
pred$UL <- plogis(pred$fit + (1.96 * pred$se.fit))


## Plot 
p1 <- ggplot(pred, aes(gap3.mean.area, PP)) + 
  geom_line(aes(col = factor(Species)), linewidth = 1.5) + 
  geom_ribbon(aes(x = gap3.mean.area, ymin = LL, ymax = UL), alpha = 0.4) + 
  facet_wrap(~Species) +
  theme_bw() +
  theme(strip.text = element_text(face = "italic"),
        legend.position="none") +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  xlab ("Scaled mean average area of gaps within 45 m of a location") +
  ylab ("Predicted use")

p1

# gap3.sd ---------------------------------------
range.gs <- range(dt1$gap3.sd.area)
range.gs
# -0.6537116  3.1268099
  
pred <- data.frame(expand.grid(
  D0 = mean(dt1$D0),
  gap3.sd.area = seq(from = -0.6537116  , to = 3.1268099, by = 0.1),
  gap3.mean.area = mean(dt1$gap3.mean.area),
  Hsd = mean(dt1$Hsd), 
  water.distance = mean(dt1$water.distance),
  Species = c("M.brandtii", "M.mystacinus"))) 
  
pred <- cbind(pred, predict(bigfit2.0, newdata = pred,
                             type = "link", se.fit = TRUE))

pred$PP <- plogis(pred$fit)
pred$LL <- plogis(pred$fit - (1.96 * pred$se.fit))
pred$UL <- plogis(pred$fit + (1.96 * pred$se.fit))


## Plot 
p2 <- ggplot(pred, aes(gap3.sd.area, PP)) + 
  geom_line(aes(col = factor(Species)), linewidth = 1.5) + 
  geom_ribbon(aes(x = gap3.sd.area, ymin = LL, ymax = UL), alpha = 0.4) + 
  facet_wrap(~Species) +
  theme_bw() +
  theme(strip.text = element_text(face = "italic"),
        legend.position="none") +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  xlab ("Scaled standard deviation of area of gaps within 45 m of a location") +
  ylab ("Predicted use")

p2


# 
# D0---------------------------------------
range.D0 <- range(dt1$D0)
range.D0
# -1.059072  3.293983
  
pred <- data.frame(expand.grid(
  D0 = seq(from = -1.059072, to = 3.293983, by = 0.1),
  gap3.sd.area = mean(dt1$gap3.sd.area),
  gap3.mean.area = mean(dt1$gap3.mean.area),
  Hsd = mean(dt1$Hsd), 
  water.distance = mean(dt1$water.distance),
  Species = c("M.brandtii", "M.mystacinus"))) 
  
pred <- cbind(pred, predict(bigfit2.0, newdata = pred,
                             type = "link", se.fit = TRUE))

pred$PP <- plogis(pred$fit)
pred$LL <- plogis(pred$fit - (1.96 * pred$se.fit))
pred$UL <- plogis(pred$fit + (1.96 * pred$se.fit))


## Plot 
p3 <- ggplot(pred, aes(D0, PP)) + 
  geom_line(aes(col = factor(Species)), linewidth = 1.5) + 
  geom_ribbon(aes(x = D0, ymin = LL, ymax = UL), alpha = 0.4) + 
  facet_wrap(~Species) +
  theme_bw() +
  theme(strip.text = element_text(face = "italic"),
        legend.position="none") +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  xlab ("Scaled canopy density within 45 m of a location") +
  ylab ("Predicted use")

p3


# Hsd ---------------------------------------
range.Hsd <- range(dt1$Hsd)
range.Hsd
# -2.125363  3.625778
  
pred <- data.frame(expand.grid(
  D0 = mean(dt1$D0),
  gap3.sd.area = mean(dt1$gap3.sd.area),
  gap3.mean.area = mean(dt1$gap3.mean.area),
  Hsd = seq(from = -2.125363, to = 3.625778, by = 0.1), 
  water.distance = mean(dt1$water.distance),
  Species = c("M.brandtii", "M.mystacinus"))) 
  
pred <- cbind(pred, predict(bigfit2.0, newdata = pred,
                             type = "link", se.fit = TRUE))

pred$PP <- plogis(pred$fit)
pred$LL <- plogis(pred$fit - (1.96 * pred$se.fit))
pred$UL <- plogis(pred$fit + (1.96 * pred$se.fit))


## Plot 
p4 <- ggplot(pred, aes(Hsd, PP)) + 
  geom_line(aes(col = factor(Species)), linewidth = 1.5) + 
  geom_ribbon(aes(x = Hsd, ymin = LL, ymax = UL, fill = factor(Species)), alpha = 0.4) + 
  facet_wrap(~Species) +
  theme_bw() +
  theme(strip.text = element_text(face = "italic"),
        legend.position="none") +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  xlab ("Scaled standard deviation of vegetation height within 45 m of a location") +
  ylab ("Predicted use")

p4

library(cowplot)

cowplot::plot_grid(p1, p2, p3, p4, nrow = 2, labels = "auto") +
  theme(text = element_text(size=20)) 
```

