---
title: "RSF_50mRadius"
output: html_document
date: "2023-12-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
### Prepare the work space
# citation()

library(tidyverse)
library(dplyr)
library(scales)
library(beepr)
library(lubridate)
library(ResourceSelection)
library(RColorBrewer)
library(cowplot)
library(colorBlindness)
library(kableExtra)
library(lme4)
library(stats)
library(DHARMa)
library(lattice)
library(broom)
library(modelsummary)
library(kableExtra)
library(gt)
library(readxl)
library(xlsx)
library(corrplot)
library(vegan)

getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/Documents/1. PhD_Main/GitHub_link/Nittedal/SpatialAndMorphology_MBRA_MMYS"

output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs"

file.name <- "RSF_50mRadius"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs/RSF_50mRadius_2023-12-22"

```


```{r}
## Covariates from LiDAR data prepared by Hans Ole 
vars <- readRDS("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Inputs/SpatialData/231220_vars_dist50_v4_na-rm.rds")

#Used and available positions - just for referencing. 
# rsf.data <- read_csv("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Outputs/HomeRangeExploration_2023-09-28/used_available_pts_combined95KE.csv", 
#      col_types = cols(...1 = col_skip()))

summary(vars)
str(vars) # sf data frame
# 16522 observations of 47 variables 

names(vars)
# [1] "BatID"             "Easting"           "Northing"          "used"              "Species"          
#  [6] "UTM"               "Hmax"              "Hmean"             "Hsd"               "Hcv"              
# [11] "Hkurt"             "Hskewness"         "H10"               "H20"               "H30"              
# [16] "H40"               "H50"               "H60"               "H70"               "H80"              
# [21] "H90"               "H95"               "D0"                "D1"                "D2"               
# [26] "D3"                "D4"                "D5"                "D6"                "D7"               
# [31] "D8"                "D9"                "gap3.n"            "gap3.mean.area"    "gap3.sd.area"     
# [36] "gap3.sum.area"     "gap5.n"            "gap5.mean.area"    "gap5.sd.area"      "gap5.sum.area"    
# [41] "ttops.n"           "crown.mean.size"   "crown.sd.size"     "ttops.mean.height" "ttops.sd.height"  
# [46] "water.distance"    "water.objtype"     "YOD"               "DIST"              "geom"           

## For writing descriptions of each variable 

#mettext <- as.data.frame(names(vars))
# write.csv(mettext, "~mettext.csv") # 15.11.2023

## First convert to a normal dataframe(drop geoms/sf objects) 
dt <- vars

dt1df <- as.data.frame(dt)
dt1df <- dt1df %>% select(-geom)
# 16522 obs of 49 vars

summary(dt1df)

## There is an -Inf value for Hmax which can be corrrected like this: 
dt1df$Hmax <- gsub("-Inf", "0.5", dt1df$Hmax)
dt1df$Hmax <- as.numeric(dt1df$Hmax)
summary(dt1df)




dt2df <- dt1df 
# 16522 obs of 49 vars

## Are there any strong outliers amongst n of local maxima? 
hist(dt2df$ttops.n) 

# How does this look for used points? 
dt2dfused <- dt2df %>% filter(used == 1)
hist(dt2dfused$ttops.n) 
# what proportion of the dataset has a ttops.n value of less than 5? 
 
openareas <- dt2df %>% filter(ttops.n <= 5)
# 3548 obs 
3548/16483
# 21.5%

# How many of these open area observations are actual used points? 
summary(openareas)
table(openareas$used) # 105 points 
 
openused <- openareas %>% filter(used == 1 ) %>%  droplevels()

summary(openused)
table(openused$Species)
  # M.brandtii M.mystacinus 
  #          69            36 
table(openused$BatID)
# Amelia Astrid  Dagny  Daisy  Ethel   Kaja Louise  Maren   Nora 
#     11      1     34      2      6      6     10      1      2 
# Phoebe  Reeda  Sofia Steffi  Stine   Thea 
#      5      1     10      8      6      2


### Think of a way to more distinctly categorize "open areas". 
ggplot(dt2df, aes(x = ttops.n, y = gap3.mean.area)) + 
  geom_point(color = "gray", alpha = 0.7) + geom_smooth(color = "black") + theme_bw()
  
## Exploring mbra used only 
mbraused <- dt2df %>% 
  dplyr::filter(Species == "M.brandtii", 
                                    used == 1) %>% 
  droplevels() #694 obs 

summary(mbraused$ttops.n)
   # Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   # 0.00   18.00   42.50   54.23   64.00  203.00 

summary(mbraused$ttops.mean.height)
  # Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  #  0.00   14.58   18.18   17.37   20.40   32.79 

## Most used points are in forests (tallest vegetation more than 14 m tall) where there are at least 18 trees (sparse forest) 


## Exploring mmys used only 
mmysused <- dt2df %>% 
  dplyr::filter(Species == "M.mystacinus", 
                                    used == 1) %>% 
  droplevels() #808 obs 

summary(mmysused$ttops.n)
   # Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   #  0.0    26.0    95.0    87.1   133.0   217.0

summary(mmysused$ttops.mean.height)
   # Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   # 0.00   16.57   18.48   18.26   20.94   26.00 

## Most used points are in forests (tallest vegetation more than 16 m tall) where there are at least 26 trees (sparse forest) 

ggplot(dt2dfused, aes(x = ttops.n, y = gap3.mean.area)) + 
  geom_point(color = "orange", alpha = 0.7) + geom_smooth(color = "black") +
  facet_wrap(~Species)

## Back to all point but look at everything below ttops.n = 175
ggplot(dt2df, aes(x = ttops.n, y = gap3.mean.area)) + 
  geom_point(color = "orange", alpha = 0.7) + geom_smooth(color = "black") + xlim(c(0,175))

## How many locations where the bats are foraging have less than 25 trees and an average gap area over 5500?
dfopen1 <- dt2dfused %>% filter(ttops.n <50,
                                gap3.mean.area > 5000) # 494 obs 
table(dfopen1$Species)
#   M.brandtii M.mystacinus 
#          295     199 

# If we use these metrics to define "open areas" then there is very little difference between the bats and not many positions in these locations. 
# Does the relationship look very different for gap5. variables?

ggplot(dt2df, aes(x = ttops.n, y = gap5.mean.area)) + 
  geom_point(color = "darkturquoise", alpha = 0.7) + geom_smooth(color = "black") 
ggplot(dt2df, aes(x = ttops.n, y = gap5.mean.area)) + 
  geom_point(color = "darkturquoise", alpha = 0.7) + geom_smooth(color = "black") + xlim(c(0,175))
dfopen2 <- dt2dfused %>% filter(ttops.n <75,
                                gap5.mean.area > 5500) 
table(dfopen2$Species)
  # M.brandtii M.mystacinus 
  #        333          221 

## Similar results at the 5 m resolution 
batcolors = c("#32A5FF", "#011f4b") 


## ttops.n
ggplot(dt2dfused) + geom_count(
  aes(x = ttops.n, y = Species, color = Species)) +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") +  theme_bw()


ggplot(dt2dfused) + geom_density(
  aes(x = ttops.n, fill = factor(Species)), alpha = 0.5) +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + theme_bw()


## gap3.mean.area
ggplot(dt2dfused) + geom_density(
  aes(x = gap3.mean.area, fill = factor(Species)), alpha = 0.5) +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  theme_bw()


#### Scale continuous variables for ordination and modelling
dt1 <- dt2df # Use this to scale all continuous numerical data 
dt1[,7:46]=scale(dt1[,7:46], scale=TRUE) #
#
# names(dt1)
```


## Correlation/collinearity between LiDAR variables 
```{r}
names(dt1)
dtc <- dt1 %>% dplyr::select(c(
  Hmax, Hmean, Hsd, Hcv, Hskewness, 
  H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
  D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
  gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
  gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
  ttops.n, ttops.mean.height, ttops.sd.height)) 

windows()

corrplot(cor(dtc))
```


# PCA ordination of available points to address collinearity and discern patterns in how variables influence each other 


### Prepare data for PCA 
```{r}

## Create an ID column so the bat meta data can be reattached later

## Create a unique row id which will become "idvar"

dt1$idvar <- paste0("ID-", 1:nrow(dt1)) 
headings <- dt1$idvar

## Now only includeLiDAR variables with IDvar
names(dt1)

dt2 <- dt1 %>% dplyr::select(c(
  Hmax, Hmean, Hsd, Hcv, Hskewness, Hkurt, 
  H10, H20, H30, H40,  H50, H60, H70, H80, H90, H95, 
  D0, D1, D2, D3, D4, D5, D6, D7, D8, D9, 
  gap3.n, gap3.mean.area,  gap3.sd.area,  gap3.sum.area,  
  gap5.n, gap5.mean.area,  gap5.sd.area,  gap5.sum.area,  
  ttops.n, ttops.mean.height, ttops.sd.height,
  crown.mean.size, crown.sd.size)) 

rownames(dt2) <- headings
# Reshape into wide format 

summary(dt2)
## This is a PCA, more info below: 

mat <- dt2 

```

## PCA
```{r}

## PCA 
trait.pca <- rda(mat) # used and available points together 
biplot(trait.pca) 
# simple plot 
screeplot(trait.pca) 
# how much of each axis describes the variation in the data 
# PC1 Explains most of the variation. Big difference between PC2 and PC3. 
summary(trait.pca)
pca.summary <- summary(trait.pca)
## In our case, 'species' are the different LiDAR variables and sites are the different bat locations. 
trait.loadings <- as.data.frame(pca.summary$species) %>% 
  mutate(trait = rownames(.))  
head(trait.loadings)
meta <- dt1 %>% dplyr::select(c(used, Species, idvar)) 
# for now, do not include bat.id
## Build meta data to be reattached in plotting
rownames(meta) <- meta$idvar
meta$gen.spe <- meta$idvar
meta$used <- as.factor(meta$used)
# Scores for all the different bat locations 
sp.scores <- as.data.frame(pca.summary$sites) %>% 
  mutate(gen.spe = rownames(.)) %>% inner_join(meta) 
# 
traittable <- trait.loadings  %>% 
  dplyr::select(trait, PC1, PC2)
#write.csv(traittable, file = file.path(output_today, "bothbats_allpts_PCA1_2_table.csv")) # 22.12.2023

### Compare trait loadings for bat locations with Pearson's correlation of PC1 and PC2, as well as of the LiDAR variables with each other 
spdf <- left_join(sp.scores, dt1, by = "idvar")
spdf1 <- spdf %>% dplyr::select(-c(PC3, PC4, PC5, PC6, idvar, gen.spe, used.x, used.y, Species.x, Species.y, BatID, Easting, Northing, UTM, YOD, DIST, water.distance, water.objtype))
#corrplot(cor(dtc))
cortab <- as.data.frame(cor(spdf1)) 
#windows()
corrplot(cor(spdf1),
         tl.col="black", tl.srt=45,  
         type="lower", col=brewer.pal(n=5, name="Greys"))
cortab1 <- cortab[1:2,]
cortab2 <- t(cortab1) # Table of the values for further comparing 
#write.csv(cortab2, file = file.path(output_today, "cortab2.csv"))
# 22.12.2023

################################################################################
##### plotting 
################################################################################

## PC1 and PC2
pca.ggplot <- ggplot(data = sp.scores, aes(x = PC1, y = PC2)) +
  geom_point() +
  geom_segment(data = trait.loadings, 
               aes(x = 0, xend = PC1/2, y = 0, yend = PC2/2), lwd = 0.1) + # this is a new geom that allows you to draw segments like the ones for the loadings above
  geom_text(data = trait.loadings, aes(x = PC1/2, y = PC2/2+0.1, label = trait), size = 3) + # this adds text to the labels
  theme_bw() 
pca.ggplot


## Table of PCA for further informing variable selection 
traittable <- trait.loadings  %>% 
  dplyr::select(trait, PC1, PC2)
#write.csv(traittable, file = file.path(output_today, "bothbats_allpts_PCA1_2_table.csv")) # 26.11.2023

## Now create a similar table for MBRA and MMYS separately 


```


## RSF
```{r}
## Simple models - separated by bat species, no species interaction 
# install.packages("lme4", type = "source") 
# library(lme4)
MBRA <- dt1 %>% filter(Species == "M.brandtii") %>% droplevels() # 7634 obs of 49 vars
MMYS <- dt1 %>% filter(Species == "M.mystacinus") %>% droplevels() # 8888 obs of 49 vars

########################################################
########################  MBRA  ########################
########################################################
fit1MBRA= glmer(used ~  
                  gap3.mean.area + 
                  D0 + H95 + Hsd + water.distance +
                  (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
fit2MBRA= glmer(used ~  
                  gap5.mean.area + 
                  D0 + H95 + Hsd + water.distance +
                  (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
# boundary (singular) fit: see help('isSingular')
isSingular(fit1MBRA)
# FALSE
isSingular(fit2MBRA)
# FALSE
AIC(fit1MBRA, fit2MBRA)
#          df      AIC
# fit1MBRA  7 4348.591 # 3 m scale is lower 
# fit2MBRA  7 4359.372 

# fit 2 has a lower AIC weight BUT it gets flagged for having a singular fit so I would instead want to use the model with the 3 m resolution gap variables. 
########################################################
########################  MMYS  ########################
########################################################


fit1MMYS= glmer(used ~  
                  gap3.mean.area + 
                  D0 + H95 + Hsd + water.distance +
                  (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
fit2MMYS= glmer(used ~  
                  gap5.mean.area +
                  D0 + H95 + Hsd + water.distance +
                  (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 
AIC(fit1MMYS, fit2MMYS)
#          df      AIC
# fit1MMYS  7 5145.626
# fit2MMYS  7 5143.210 # 5 m scale is lower 

         # The difference between the weights is negligible, I feel comfortable sticking with the 3 m resolution due to the singularity issues found in the M. brandtii models. 
################################################
# The gap5 model for MBRA throws a singularity warning, and the AIC weights between the model pairs is very little so I will use the 3 m resolution models to continue. 

summary(fit1MBRA)

summary(fit1MMYS)

sjPlot::tab_model(fit1MBRA, fit1MMYS,fit2MBRA, fit2MMYS,
                  dv.labels = c(
                    "Myotis brandtii - 3 m", "Myotis mystacinus - 3 m",
                    "Myotis brandtii - 5 m", "Myotis mystacinus - 5 m"), transform = NULL, auto.label = FALSE) 
```


## Use the VIF function to test for correlation amongst variables 
```{r}
library(car)
### VIF equal to 1 = variables are not correlated.
## VIF between 1 and 5 = variables are moderately correlated.
## VIF greater than 5 = variables are highly correlated.


vif(fit1MBRA)
# gap3.mean.area             D0            H95            Hsd water.distance 
#       2.741990       2.413678       6.131832       5.201883       1.152878 
vif(fit1MMYS)
# gap3.mean.area             D0            H95            Hsd water.distance 
#       2.464688       3.025031       4.715925       3.863640       1.249359 


(bigfit2)

# Fixed effects:
#                                    Estimate Std. Error z value Pr(>|z|)    
# (Intercept)                        -2.36989    0.06354 -37.300  < 2e-16 ***
# SpeciesM.mystacinus                -0.20330    0.08833  -2.302   0.0214 *  
# gap3.mean.area                     -0.61737    0.07116  -8.676  < 2e-16 ***
# D0                                 -0.44494    0.07080  -6.284 3.30e-10 ***
# Hsd                                 0.25406    0.04561   5.570 2.54e-08 ***
# water.distance                     -0.51920    0.03588 -14.471  < 2e-16 ***
# SpeciesM.mystacinus:gap3.mean.area  0.43080    0.09966   4.323 1.54e-05 ***
# SpeciesM.mystacinus:D0              0.60367    0.09596   6.291 3.16e-10 ***
# SpeciesM.mystacinus:Hsd             0.13839    0.06488   2.133   0.0329 *  
   
# Drop H95 to see how this changes the correlation amongst variables 
fit3MBRA= glmer(used ~  
                  gap3.mean.area + 
                  D0 + Hsd + water.distance +
                  (1|BatID), data=MBRA,
              family=binomial(link="logit"),nAGQ = 0) 
fit3MMYS= glmer(used ~  
                  gap3.mean.area + 
                  D0 + Hsd + water.distance +
                  (1|BatID), data=MMYS,
              family=binomial(link="logit"),nAGQ = 0) 


vif(fit3MBRA)
# gap3.mean.area             D0            Hsd water.distance 
#       2.513972       2.334639       1.111466       1.135041  
vif(fit3MMYS)
# gap3.mean.area             D0            Hsd water.distance 
#       2.503120       2.605929       1.076558       1.235351 


## Sorted 

bigfit1 = glmer(used ~  Species + 
                  gap3.mean.area + 
                  D0 + Hsd + water.distance +
                  Species*gap3.mean.area + 
                  Species*D0 + 
                  Species*Hsd + 
                  Species*water.distance +
                  (1|BatID), data=dt1,
              family=binomial(link="logit"),nAGQ = 0)
summary(bigfit1)
## Now step-wise selection with AIC 
drop1(bigfit1)
# used ~ Species + gap3.mean.area + gap3.sd.area + D0 + Hsd + water.distance + 
#     Species * gap3.mean.area + Species * gap3.sd.area + Species * 
#     D0 + Species * Hsd + Species * water.distance + (1 | BatID)
# 
#                        npar    AIC
# <none>                      9565.6
# Species:gap3.mean.area    1 9581.0
# Species:D0                1 9604.8
# Species:Hsd               1 9567.4
# Species:water.distance    1 9564.5 ** 

# Drop interaction between species and distance to water
  
bigfit2 =  glmer(used ~  Species + 
                   gap3.mean.area + 
                   D0 + Hsd + water.distance +
                   Species*gap3.mean.area + 
                   Species*D0 + 
                   Species*Hsd + 
                   (1|BatID), data=dt1,
               family=binomial(link="logit"),nAGQ = 0)


drop1(bigfit2)
# boundary (singular) fit: see help('isSingular')
## Suggests to keep everything 
#                        npar    AIC
# <none>                      9545.9 # Do not drop any further 
# water.distance            1 9746.2
# Species:gap3.mean.area    1 9572.8
# Species:gap3.sd.area      1 9558.9
# Species:D0                1 9599.5
# Species:Hsd               1 9546.6

summary(bigfit2)

sjPlot::tab_model(bigfit2, transform = NULL, auto.label = FALSE, show.re.var = TRUE,   show.fstat = TRUE, show.stat = TRUE) 

```



```{r}
### Model diagnostics for 
simulationOutput <- simulateResiduals(fittedModel = bigfit2, plot = T)
### Help with interpretation of residuals vs. predicted: 
# https://stats.stackexchange.com/questions/449208/diagnostic-plot-residual-vs-predicted-of-a-glmm-using-dharma
### recalculateResiduals()
# KS test -  the p-value shows you that there is *not* a significant deviation from the assumed distribution
# Dispersion test – Not over or underdispersed
# Outlier – No indication of outliers 
# 
# Residuals appear to more or less agree with predicted values 
#windows()
testDispersion(simulationOutput)
# 
# 	DHARMa nonparametric dispersion test via sd of residuals fitted vs.
# 	simulated
# 
# data:  simulationOutput
# dispersion = 0.9964, p-value = 0.944
# alternative hypothesis: two.sided
# no strong evidence for Dispersion issues 
testZeroInflation(simulationOutput)
# 	DHARMa zero-inflation test via comparison to expected zeros with simulation
# 	under H0 = fitted model
# 
# data:  simulationOutput
# ratioObsSim = 1.0012, p-value = 0.816
# alternative hypothesis: two.sided
# No strong evidence for zero inflation 
testQuantiles(simulationOutput)
# 	Test for location of quantiles via qgam
# 
# data:  simulationOutput
# p-value < 2.2e-16
# alternative hypothesis: both
## Evidence found that there are strong deviations from residuals and predicted values** 
# "A significant p-value for the splines means the fitted spline deviates from a flat line at the expected location (p-values of intercept and spline are combined via Benjamini & Hochberg adjustment to control the FDR)
#The p-values of the splines are combined into a total p-value via Benjamini & Hochberg adjustment to control the FDR."
testCategorical(simulationOutput, catPred = dt1$BatID)
## No bat IDs had a low p value for the Asymptotic  one-sample Kolmogorov-Smirnov test
testCategorical(simulationOutput, catPred = dt1$Species)
## No bat species had a low p value for the Asymptotic  one-sample Kolmogorov-Smirnov test

vif(bigfit2)
        #        Species         gap3.mean.area                     D0                    Hsd 
        #       1.095477               5.148412               5.380427               2.109284 
        # water.distance Species:gap3.mean.area             Species:D0            Species:Hsd 
        #       1.174590               5.280176               5.574119               2.127375 


# Higher VIF values for interacting terms is not too much of a concern 

```


## Plot predictions using glm 
```{r}
## Refitting the model with GLM to sketch results
bigfit2.0<- glm(used ~  Species + 
                   gap3.mean.area + 
                   D0 + Hsd + water.distance +
                   Species*gap3.mean.area + 
                   Species*D0 + 
                   Species*Hsd, 
                  family=binomial(), data=dt1)
summary(bigfit2.0)
# Call:
# glm(formula = used ~ gap3.mean.area + gap3.sd.area + D0 + H95 + 
#     Hsd + water.distance, family = binomial(), data = MMYS)
# 
# Coefficients:
#                Estimate Std. Error z value Pr(>|z|)    
# (Intercept)                        -2.35509    0.04372 -53.863  < 2e-16 ***
# SpeciesM.mystacinus                -0.20973    0.06144  -3.414 0.000641 ***
# gap3.mean.area                     -0.64842    0.06835  -9.487  < 2e-16 ***
# D0                                 -0.45603    0.07056  -6.463 1.03e-10 ***
# Hsd                                 0.24518    0.04457   5.502 3.76e-08 ***
# water.distance                     -0.48724    0.03492 -13.952  < 2e-16 ***
# SpeciesM.mystacinus:gap3.mean.area  0.47468    0.09738   4.875 1.09e-06 ***
# SpeciesM.mystacinus:D0              0.58313    0.09526   6.122 9.26e-10 ***
# SpeciesM.mystacinus:Hsd             0.13679    0.06382   2.143 0.032079 * 
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# (Dispersion parameter for binomial family taken to be 1)
# 
#     Null deviance: 5408.0  on 8849  degrees of freedom
# Residual deviance: 5104.5  on 8843  degrees of freedom
# AIC: 5118.5
# 


# Number of Fisher Scoring iterations: 6
batcolors = c("#32A5FF", "#011f4b") 

# New facet label names for supp variable
supp.labs <- c("M. brandtii", "M. mystacinus")
names(supp.labs) <- c("M.brandtii", "M.mystacinus")
### Plotting predictions ####
# gap3.mean ---------------------------------------
range.gm <- range(dt1$gap3.mean.area)
range.gm
# -1.040815  1.198892
  
pred <- data.frame(expand.grid(
  D0 = mean(dt1$D0),
  gap3.mean.area = seq(from = -1.040815  , to = 1.198892, by = 0.1),
  Hsd = mean(dt1$Hsd), 
  water.distance = mean(dt1$water.distance),
  Species = c("M.brandtii", "M.mystacinus"))) 
  
pred <- cbind(pred, predict(bigfit2.0, newdata = pred,
                             type = "link", se.fit = TRUE))
pred$PP <- plogis(pred$fit)
pred$LL <- plogis(pred$fit - (1.96 * pred$se.fit))
pred$UL <- plogis(pred$fit + (1.96 * pred$se.fit))
## Plot 
p1 <- ggplot(pred, aes(gap3.mean.area, PP)) + 
  geom_line(aes(col = factor(Species)), linewidth = 1.5) + 
  geom_ribbon(aes(x = gap3.mean.area, ymin = LL, ymax = UL,
              fill = factor(Species)), alpha = 0.4)  +
  facet_wrap(~Species, labeller = labeller(Species = supp.labs)) +
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01,
                                 decimal.mark = '.')) +
  theme_bw() +
  theme(strip.text = element_text(face = "italic"),
        legend.position="none") +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  xlab ("Mean average area of gaps within 45 m of a location") +
  ylab ("Predicted probability of use") +
  xlab ("gap3.mean.area") +
  ylab ("Probability of use") +
  theme(text = element_text(size=20))
p1

# distance to water ---------------------------------------
range.gs <- range(dt1$water.distance)
range.gs
# 1.282820  3.698758
  
pred <- data.frame(expand.grid(
  D0 = mean(dt1$D0),
  gap3.mean.area = mean(dt1$gap3.mean.area),
  Hsd = mean(dt1$Hsd), 
  water.distance = seq(from = 1.282820  , to = 3.698758, by = 0.1),
  Species = c("M.brandtii", "M.mystacinus"))) 
  
pred <- cbind(pred, predict(bigfit2.0, newdata = pred,
                             type = "link", se.fit = TRUE))
pred$PP <- plogis(pred$fit)
pred$LL <- plogis(pred$fit - (1.96 * pred$se.fit))
pred$UL <- plogis(pred$fit + (1.96 * pred$se.fit))

## Plot 
p2 <- ggplot(pred, aes(water.distance, PP)) + 
  geom_line(aes(col = factor(Species)), linewidth = 1.5) + 
  geom_ribbon(aes(x = water.distance, ymin = LL, ymax = UL, 
              fill = factor(Species)), alpha = 0.4) +
  facet_wrap(~Species,labeller = labeller(Species = supp.labs)) +
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01,
                                 decimal.mark = '.')) +
  theme_bw() +
  theme(strip.text = element_text(face = "italic"),
        legend.position="none") +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  xlab ("Distance to water") +
  ylab ("Probability of use") +
  theme(text = element_text(size=20))
p2


# D0---------------------------------------
range.D0 <- range(dt1$D0)
range.D0
# -0.9838802  3.3390781
  
pred <- data.frame(expand.grid(
  D0 = seq(from = -0.9838802, to = 3.3390781, by = 0.1),
  gap3.sd.area = mean(dt1$gap3.sd.area),
  gap3.mean.area = mean(dt1$gap3.mean.area),
  Hsd = mean(dt1$Hsd), 
  water.distance = mean(dt1$water.distance),
  Species = c("M.brandtii", "M.mystacinus"))) 
  
pred <- cbind(pred, predict(bigfit2.0, newdata = pred,
                             type = "link", se.fit = TRUE))
pred$PP <- plogis(pred$fit)
pred$LL <- plogis(pred$fit - (1.96 * pred$se.fit))
pred$UL <- plogis(pred$fit + (1.96 * pred$se.fit))
## Plot 
p3 <- ggplot(pred, aes(D0, PP)) + 
  geom_line(aes(col = factor(Species)), linewidth = 1.5) + 
  geom_ribbon(aes(x = D0, ymin = LL, ymax = UL,
                  fill = factor(Species)), alpha = 0.4) + 
  facet_wrap(~Species, labeller = labeller(Species = supp.labs)) +
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01,
                                 decimal.mark = '.')) +
  theme_bw() +
  theme(strip.text = element_text(face = "italic"),
        legend.position="none") +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  xlab ("Canopy density within 45 m of a location") +
  ylab ("Predicted probability of use") +
  xlab ("D0") +
  ylab ("Probability of use") +
  theme(text = element_text(size=20))
p3

# Hsd ---------------------------------------
range.Hsd <- range(dt1$Hsd)
range.Hsd
# -2.125363  3.625778
  
pred <- data.frame(expand.grid(
  D0 = mean(dt1$D0),
  gap3.sd.area = mean(dt1$gap3.sd.area),
  gap3.mean.area = mean(dt1$gap3.mean.area),
  Hsd = seq(from = -2.125363, to = 3.625778, by = 0.1), 
  water.distance = mean(dt1$water.distance),
  Species = c("M.brandtii", "M.mystacinus"))) 
  
pred <- cbind(pred, predict(bigfit2.0, newdata = pred,
                             type = "link", se.fit = TRUE))
pred$PP <- plogis(pred$fit)
pred$LL <- plogis(pred$fit - (1.96 * pred$se.fit))
pred$UL <- plogis(pred$fit + (1.96 * pred$se.fit))
## Plot 
p4 <- ggplot(pred, aes(Hsd, PP)) + 
  geom_line(aes(col = factor(Species)), linewidth = 1.5) + 
  geom_ribbon(aes(x = Hsd, ymin = LL, ymax = UL, 
                  fill = factor(Species)), alpha = 0.4) + 
  facet_wrap(~Species, labeller = labeller(Species = supp.labs)) +
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01,
                                 decimal.mark = '.')) +
  theme_bw() +
  theme(strip.text = element_text(face = "italic"),
        legend.position="none") +
  scale_colour_manual(values = 
                        batcolors,  
                      aesthetics = c("fill", "colour"), 
                      name = "Bat species") + 
  xlab ("Standard deviation of vegetation height within 45 m of a location") +
  ylab ("Predicted probability of use") +
  xlab ("Hsd") +
  ylab ("Probability of use") +
  theme(text = element_text(size=20))
p4

library(cowplot)
windows()
cowplot::plot_grid(p1, p2, p3, p4, nrow = 4, 
                   labels = c("a.", "b.", "c.", "d."), 
                   label_x = 0.08, label_y = 0.08,
                   hjust = -0.5, vjust = -0.5) +
  theme(text = element_text(size=16)) 

```



## Compare home ranges

"A Mann-Whitney U test (sometimes called the Wilcoxon rank-sum test) is used to compare the differences between two independent samples when the sample distributions are not normally distributed and the sample sizes are small (n <30).

It is considered to be the nonparametric equivalent to the two-sample independent t-test." 
# https://www.statology.org/mann-whitney-u-test-r/ 

```{r}
HR <- read_excel("C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/1. Nittedal 2018-2020/Nittedal_Main/Analyses/Inputs/HomerangeOverview.xlsx", 
     col_types = c("text", "text", "text", 
         "numeric", "text", "numeric", "numeric", 
         "text", "numeric", "numeric"))
HR$Species <- as.factor(HR$Species)
HR$BatID <- as.factor(HR$BatID)
mbrahr <- HR %>% 
  filter(Species == "M.brandtii") %>% 
  droplevels() %>% 
  select(HRarea) 
mbrahr <- mbrahr$HRarea

mmyshr <- HR %>% 
  filter(Species == "M.mystacinus") %>% 
  droplevels() %>% 
  select(HRarea) 
mmyshr <- mmyshr$HRarea
# 

summary(mbrahr)
 # Min.   : 0.110  
 # 1st Qu.: 1.600  
 # Median : 1.940  
 # Mean   : 3.999  
 # 3rd Qu.: 5.230  
 # Max.   :12.740  
summary(mmyshr)
 # Min.   :0.0800  
 # 1st Qu.:0.3675  
 # Median :0.5150  
 # Mean   :0.7175  
 # 3rd Qu.:1.0975  
 # Max.   :1.8700  
# 	Wilcoxon rank sum exact test

wilcox.test(mbrahr, mmyshr)
# 
# data:  mbrahr and mmyshr
# W = 92, p-value = 0.00562
# alternative hypothesis: true location shift is not equal to 0
# There is strong evidence that the home range size between the two species is distinct from each other. 
```

